---
title: "Home Office"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 1
    include:
      after_body: footer/_footer_Richard.txt
bibliography: footer/references.bib
csl: footer/apa.csl    
---
<!-- "after body" is referencing what should stand in the end of the page. I created a .txt file with some HTML-Code, indicating the copyright of the page and who is responsible for this particular site (in this case, me) -->
<!-- "bibliography" takes the references.bib I created with Citavi and creates a bibliography (oh surprise) of the citations used in the text -->
<!-- "csl: apa.csl" makes the citation apa-compatible (using the mentioned .csl file) -->
<style type="text/css">
  a {
    color: #3182bd;
    background-color: transparent;
    text-decoration: none;
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
library(ggplot2)
library(plyr)
library(dplyr)
library(plotly)
library(tidyr)
library(hrbrthemes)
library(gganimate)
library(magick)
library(tibble)
library(patchwork)

options(scipen = 999)
data_HO = read.csv("data/data_Homeoffice.csv")
data_HO = distinct(data_HO, ID, .keep_all = T)
months_compl = c("April '20", "May '20", "June '20", "July '20", "August '20", "September '20", "October '20", "November '20", "December '20", 
                 "January '21", "February '21", "March '21", "April '21", "May '21", "June '21") 
#For plots where the data for june is extrapolated

months_miss = c("April '20", "May '20", "July '20", "August '20", "September '20", "October '20", "November '20", "December '20", 
                "January '21", "February '21", "March '21", "April '21", "May '21", "June '21") 
#For operations where only the observed data is used, see e.g. "Distributions over Time"

font_colour = theme(text = element_text(colour = "#3e3f3a")) 
#Standard font colour of the text as indicated by the theme. Add to any gg plot to make all text in it the same colour as the "normal" body-text. MAY OVERRIDE POTENTIAL INTENDED FONTCOLOURS IN INDIVIDUAL PLOTS    
```

# Introduction 

With the increasing digitalization of work, the idea of __working from home__ gained more and more traction. For some, it's a convenience in the face of unnecessary commuting to work (e.g. when you're a programmer, who doesn't need to come into work every day while working on a software), for others it can be a crucial part in balancing out work and family demands. It surely has its advantages and disadvantages, both for the worker and for the company, but having it as a possibility increases flexibility and adaptability.   
  
With the global COVID-19 pandemic, __working from home__ drastically shifted from mere convenience to a __necessity__ in many cases, as social distancing guidelines were imposed and businesses had to shut down. This put additional interest into the topic of Home Office - how it's being implemented, what effect it has on the workers and how it can be improved on.  
  
Beginning in our third wave of inquiry in __April__, we started to ask our participants various questions about their __experience regarding Home Office__. With the exception of June, where a part of the questions needed to be reduced in order to gather data on work and ageing, we then continued presenting our participants the same items monthly. Below, You can see some __descriptive statistics__ about various topics connected to working from home. Please note that these results present only an __overview of our data__, and causal interpretations can exclusively be made after rigorous analysis, published elsewhere. Feel free, however, to get inspirations for future research!  


  
***
<!-- .tabset and .tabset fade creates tabs, where content will be stored. -->
<!-- The individual tabs are marked by headers one level under the tabset, in this case the tabset is at level 1 and all subsequent level 2 headers will be presented as tabs under the tabset, until another level 1 header is written. -->
<!-- The "{-}" after "Plot" prevents this level 2 header to be counted when counting through the individual headers -->
  
  
  

# Average Time Spent in Home Office {.tabset .tabset-fade}
## Plot {-}

```{r Percent-HO, include=TRUE, fig.show='hold', out.width = c('50%','50%'), fig.cap= "Percentage of time worked from home in December 2019"}
home_office_T1 = data.frame(
  label = c("In Home Office", "Out of Home Office"),
  percent = round(c(mean(data_HO$T1_home_office, na.rm = T),100-mean(data_HO$T1_home_office, na.rm = T)), digits = 2)
)

home_office_T1 <- home_office_T1 %>% 
  arrange(desc(label)) %>%
  mutate(ypos = cumsum(percent)- 0.5*percent)
# Code for making the numbers in the pie chart nicely positioned

home_office_T1$ypos = c(44.2,92.5) 
#Nicer positioning of the labels inside the Pie-Chart by manually adjusting the calculated values from above

mean_HO_T1 = ggplot(home_office_T1, aes(x="", y=percent, fill = label))+    
  #aes(x="",...) for pie chart
  geom_bar(width = 1, stat = "identity", color = "white", alpha = .9) +     
  #stat = "identity" for taking the exact numbers from the dataframe, without further calculations; color = "white" for the outlining
  scale_fill_manual(values = c("#bdd7e7","#3182bd"))+                       
  #colours taken from colour_scale_brewer, Blue. Names of colours taken from https://colorbrewer2.org/#type=sequential&scheme=Blues&n=5
  coord_polar("y", direction = -1)+
  # direction of the parts
  geom_text(aes(y = ypos, label = paste0(percent, '%')), size=6, colour = "#3e3f3a") +
  # paste0 for creating (a vector of) strings out of numeral data
  # For some reason, font_colour didn't overwrite the font colour inside the chart (earlier it did...)
  guides(fill=guide_legend(title="Average proportion of worktime spent...", title.position = "top"))+
  theme_void()+
  # losing all other lines for sleeker look
  theme(legend.position="bottom", legend.text = element_text(size = 14), legend.title = element_text(size = 14.5))+
  font_colour
  

mean_HO_T1
# presenting the plot

density_HO_T1 = ggplot(data_HO, aes(T1_home_office))+
  theme_classic()+
  geom_histogram(binwidth=10,col="#3182bd", fill = "#6baed6", alpha = .4)+
  # binwidth = how wide should the individual coloums be? col for the linecolour, fill for the filled colour
  geom_vline(aes(xintercept=mean(T1_home_office, na.rm=T)), linetype="dashed", size= 0.5)+ #Line representing the mean
  labs(x="Percentage of worktime spent in Home Office", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,100,10), labels = paste0(seq(0,100,10), '%')) +
  # Indicating the scale size and labels; seq to be read like: "Make a sequence from 0 to 100, going in steps of 10
  scale_y_continuous(breaks=seq(0, 1500, 250))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour
  
  
density_HO_T1


```
  
&nbsp;  
&nbsp;  
<!-- &nbsp;  (attention, two spaces afterwards are very important!) is a more reliable way for making line breaks - double spacing doesn't always work out very well  -->
<!-- In order to have less text, the information can be viewed by klicking on this tab. For that to work, there is an R-Chunk which just presents the graphs from above with the desired text around it. -->
<!-- If you find a better way to make text appear and disappear, feel free to tell me! -->

## Additional Information {-}  
In December of 2019, when the coronavirus was just one of many news stories from abroad, we coincidentally asked the participants of our study:  
___"What percentage of Your worktime do You work from home (Home Office)?"___  
The following graphs show the __average proportion of time__ spent in Home Office and how the percentages were __distributed__ back then.  

```{r Percent-HO2, include=TRUE, fig.show='hold', out.width = c('50%','50%'), fig.cap= "Percentage of time worked from home in December 2019", cache.whatever= density_HO_T1}
## For details on the code for the plots, please change to the "Plots"-Tab and unfold the code there. ##

#cache.whatever inside the chunk options tells the chunk, that it has to be invalidated, as soon as one of these variables change. Otherwise, changing the plots in the chunk above doesn't invalidate this chunk and the lastly cached version will be displayed.


mean_HO_T1
density_HO_T1

```


As can be seen, before the COVID-19 Crisis hit, __work from home was rather sparse__. Only `r length(na.omit(data_HO[data_HO$T1_home_office>0,3]))` of the `r length(na.omit(data_HO$T1_home_office))` participants, who answered this question, had indicated that they worked from home at all (equaling `r round((length(na.omit(data_HO[data_HO$T1_home_office>0,2]))/length(na.omit(data_HO$T1_home_office)))*100,digits = 2)`%)  
  
<!-- To end the tabset from above without starting a new level 1 header, the following line of code is needed. .unnumbered is equivalent to {-} and .toc-ignore makes the toc not include this header. This is necessary, since we told the toc to include all level 1 headers, so otherwise there would be an ugly space in the toc, leading to this point in the page -->
# {.unnumbered .toc-ignore}

## Development over Time {.tabset .tabset-fade}

### Plots {-}

```{r Percentage over Time, include = TRUE, out.width='100%', fig.height=3.5, cache.whatever= months_miss}
#HO6
HO_Perc = select(data_HO,ends_with("_HO6"))
# grep searches for patterns in a given Vector (in this case, the pattern "_HO6" in names(data_HO)). This allows easy finding of the same variable over different time points 


HO_Perc_rel = data.frame(
  matrix(
    NA,
    nrow = length(months_compl),
    ncol = 5,
    dimnames = list(c(),c("month","mean_perc", "sd_perc", "missing", "mis_sd"))
  )
)
HO_Perc_rel$month = as.factor(months_compl)

for (i in 1:length(months_compl)) {
  #means
  if (HO_Perc_rel[i,1] %in% months_miss) {
    HO_Perc_rel[i,2] = mean(HO_Perc[,paste0("T",i+2,"_HO6")], na.rm = T)
  } 
  
  #sds
  if (HO_Perc_rel[i,1] %in% months_miss) {
    HO_Perc_rel[i,3] = sd(HO_Perc[,paste0("T",i+2,"_HO6")], na.rm = T)
  } 
}


for (i in 1:length(months_compl)) {
  #missing mean
  if (HO_Perc_rel[i,1] %in% c("May '20","July '20")) {
    HO_Perc_rel[i,4] = HO_Perc_rel[i,2]
    
  } else if (HO_Perc_rel[i,1] == "June '20"){
    HO_Perc_rel[i,4] = mean(c(HO_Perc_rel[i-1,2],HO_Perc_rel[i+1,2]))
    
  } 
  
  #missing sd
  if (HO_Perc_rel[i,1] %in% c("May '20","July '20")) {
    HO_Perc_rel[i,5] = HO_Perc_rel[i,3]
    
  } else if (HO_Perc_rel[i,1] == "June '20"){
    HO_Perc_rel[i,5] = mean(c(HO_Perc_rel[i-1,3],HO_Perc_rel[i+1,3]))
    
  } 
}


HO_Perc_plot = ggplot(HO_Perc_rel, aes(x=month, y = mean_perc)) + 
  geom_line(aes(group=1), col= "#3182bd", size = 1.5)+
  geom_line(aes(x=month, y=missing, group =1,color = "#3182bd"), col= "#3182bd", size = 1.5, linetype = "dashed" )+
  # for the connecting dashed line
  geom_point(col= "#3182bd", size = 3)+
  # for the points at every month
  geom_ribbon(aes(y=mean_perc, ymin = mean_perc - (sd_perc/2), ymax = mean_perc + (sd_perc/2), group = 1),fill="#3182bd", alpha=0.4) +
  geom_ribbon(aes(y=missing, ymin = missing - (mis_sd/2), ymax = missing + (mis_sd/2), group = 1),fill="#3182bd", alpha=0.3) +
  # only half a SD around the mean, because the whole SD would have filled the whole scale
  coord_cartesian(ylim = c(0,60))+
  theme_minimal()+
  scale_x_discrete(limits = months_compl, name ="" )+
  scale_y_continuous(breaks = seq(0,60,10), labels = paste0(seq(0,60,10), "%"), name = "Percentage of a week \nworked from home")+
  labs(caption = "Note: Data was missing for June. Ribbon represents 1SD around the mean.")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  font_colour

HO_Perc_plot


## Old way of calculating the Means/SDs and extrapolating their missing value in between.
## New code with for- and if-constructions should calculate all the required data by itself, but as a safety, we leave this old code here
# HO_Perc_rel = data.frame(
#   month = as.factor(months_compl),
#   mean_perc = c(
#     mean(HO_Perc$T3_HO6, na.rm = T),
#     mean(HO_Perc$T4_HO6, na.rm = T),
#     NA,
#     mean(HO_Perc$T6_HO6, na.rm = T),
#     mean(HO_Perc$T7_HO6, na.rm = T),
#     mean(HO_Perc$T8_HO6, na.rm = T),
#     mean(HO_Perc$T9_HO6, na.rm = T),
#     mean(HO_Perc$T10_HO6, na.rm = T),
#     mean(HO_Perc$T11_HO6, na.rm = T),
#     mean(HO_Perc$T12_HO6, na.rm = T)
#   ),
#   sd_perc = c(
#     sd(HO_Perc$T3_HO6, na.rm = T),
#     sd(HO_Perc$T4_HO6, na.rm = T),
#     NA,
#     sd(HO_Perc$T6_HO6, na.rm = T),
#     sd(HO_Perc$T7_HO6, na.rm = T),
#     sd(HO_Perc$T8_HO6, na.rm = T),
#     sd(HO_Perc$T9_HO6, na.rm = T),
#     sd(HO_Perc$T10_HO6, na.rm = T),
#     sd(HO_Perc$T11_HO6, na.rm = T),
#     sd(HO_Perc$T12_HO6, na.rm = T)
#   )
# ) 
# # Data-Frame with the means and standard deviations of the percentages of time Worked in Home Office, Long Format (Because of the many NAs, ggplots stat = "mean" could have shown errrors)
# # Usually Colmeans would have maybe done the trick, but we don't have the data for every month, and need an NA, so that we can fill that with in the plot
# 
# # For every new wave, that is entered, this new TX_HOY needs to be added in these dataframes and NAs in the "Missing" cols
# 
# HO_Perc_rel$missing = c(NA, 
#                         HO_Perc_rel[2,2],
#                         mean(c(HO_Perc_rel[2,2],HO_Perc_rel[4,2])),
#                         HO_Perc_rel[4,2],
#                         NA,
#                         NA,
#                         NA,
#                         NA,
#                         NA,
#                         NA) 
# #Extrapolating the missing value in June to make a separate connecting line between May and July in the graph
# HO_Perc_rel$mis_sd = c(NA, 
#                        HO_Perc_rel[2,3],
#                        mean(c(HO_Perc_rel[2,3],HO_Perc_rel[4,3])),
#                        HO_Perc_rel[4,3],
#                        NA,
#                        NA,
#                        NA,
#                        NA,
#                        NA,
#                        NA)
```
  

  
&nbsp;  

```{r distributions over Time, fig.show= 'hold', out.width=c('100%','50%','50%'),cache.whatever= HO_Perc_plot}

HO_Perc_long = gather(HO_Perc, month, percentage)
HO_Perc_long$month = factor(HO_Perc_long$month, levels = names(HO_Perc), labels = months_miss)

## Here are some attempts to show the distribution of the percentages over time, to show that the middle part of the distribution remained sparse and only the right border grew, accounting for the overall increase in Home Office time. 

HO_Perc_ani = ggplot(HO_Perc_long, aes(percentage)) +
  theme_classic()+
  geom_histogram(binwidth=10,col="#3182bd", fill = "#6baed6", alpha = .4)+
  labs(x="Percentage of worktime spent in Home Office", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,100,10), labels = paste0(seq(0,100,10), '%')) +
  scale_y_continuous(breaks=seq(0, 1500, 250))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour +
# normal ggplot plot
  transition_states(month,
                    transition_length = 2,
                    state_length = 1) +
# by adding this part, it becomes a animated plot. the first argument indicates, by which variable the states should be calculated
  ggtitle('{closest_state}') +
# for the title to indicate the respective month
  ease_aes('cubic-in-out')
# for nicer transitioning

animate(HO_Perc_ani, renderer = magick_renderer(), duration = length(months_compl), fps = 10)

HO_Perc_dens = ggplot(HO_Perc_long, aes(percentage, y=..density.., fill = month, color = month)) +
  theme_classic()+
  theme(legend.title = element_blank())+
  geom_density(alpha = .1)+
  labs(x="Percentage of worktime spent in Home Office", y = "Density", legend = NULL)+
  scale_x_continuous(breaks = seq(0,100,10), labels = paste0(seq(0,100,10), '%')) +
  scale_fill_brewer(palette="Blues", direction = -1) +
  scale_color_brewer(palette="Blues", direction = 1) +
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour

HO_Perc_dens

HO_Perc2 = select(data_HO, ID, ends_with("_HO6"))
HO_Perc2 = add_column(HO_Perc2, T5_HO6 = NA, .before = "T6_HO6")
HO_Perc2$T5_HO6 = as.numeric(HO_Perc2$T5_HO6)

HO_Perc_long2 = reshape(
  HO_Perc2,
  varying = grep("HO6", names(HO_Perc2), value = T),
  v.names = "Percentage",
  idvar = "ID",
  direction = "long",
  timevar = "month"
  
)

HO_Perc_long2$month = factor(HO_Perc_long2$month, labels = months_compl)

HO_perc_violplot = ggplot(HO_Perc_long2, aes(month,Percentage)) +
  geom_violin(trim = T,col= "#6baed6" ) +
  geom_jitter(width = 0.05, size = 0.05,col= "#3182bd", alpha = 0.3) +
  
  geom_line(aes(group = 1), stat = "summary", fun = mean, col= "#3182bd", size = 1)+
  geom_point(col= "#3182bd", size = 2.5, stat = "summary", fun = mean)+
  
  geom_line(aes(group = 1), stat = "summary", fun = median, col= "#6baed6", size = 1, linetype = 4)+
  geom_point(col= "#6baed6", size = 2.5, stat = "summary", fun = median, shape = 18)+
  # for the points at every month
    # only half a SD around the mean, because the whole SD would have filled the whole scale
  coord_cartesian(ylim = c(0,100))+
  theme_minimal()+
  scale_x_discrete(limits = months_compl, name ="" )+
  scale_y_continuous(breaks = seq(0,100,10), labels = paste0(seq(0,100,10), "%"), name = "Percentage of a week worked from home")+
  labs(caption = "Note: Data was missing for June. Upper line represents means, lower line represents medians")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  font_colour

HO_perc_violplot


```


&nbsp;  
&nbsp;    
  
### Additional Information {-}
Since December, the first time we asked our participants about their work in the Home Office again was in April of 2020, and then, with the exception of June, monthly. Specifically, we wanted to know:  
___"In the past 4 weeks (Since the beginning of ...): What percentage of Your average work week did you spend in Home Office?"___

```{r Percentage over Time 2, include = TRUE, out.width='100%', fig.height=3.5,cache.whatever= HO_Perc_plot}
## For details on the code for the plots, please change to the "Plots"-Tab and unfold the code there. ##

HO_Perc_plot

```
  
  
Notably and expectedly, the mean __time spent in Home Office grew__ as the pandemic unfolded. At its peak in __May__, the percentage was __three times as high as in December__. Furthermore, as infection rates dropped in the summer and some form of "new normality" emerged, working from home steadily declined. Remembering, however, how disproportionate the various rates were distributed in December, it would be interesting to look at how the __distribution changed over time__:

```{r distributions over Time 2, fig.show= 'hold', out.width=c('100%','50%','50%'), cache.whatever= HO_Perc_dens}
## For details on the code for the plots, please change to the "Plots"-Tab and unfold the code there. ##

animate(HO_Perc_ani, renderer = magick_renderer(), duration = length(months_compl), fps = 10)
HO_Perc_dens
HO_perc_violplot

```

Looking at these distributions it grows clear that the increased percentage worked from home was mainly driven by the outer right part of the distribution, i.e. the people who __worked from home entirely__, while the rest continued working fully at their regular workplace.  

Moreover, the decrease over time seems to be attributed to the workers, who returned from their Home Offices, while the __middle__ of the distribution remained largely __unchanged__. Note that the steep increase in October was partially due to a resampling of new participants in order to compensate for the gradual dropout.
  
___
  
## {-}
  
  

```{r shinyPerc, eval=FALSE, cache=FALSE, include=FALSE}

selectInput(
  "month", label = "Month",
  choices = c("April"=1,"May"=2,"July"=3, "August"=4, "September"=5), selected = "April"
)
sliderInput(
  "month2", label = "Timepoint", min = 1, max = 5, value = 1, step = 1
)

colnames(HO_Perc) = c(1:5)

reactive_data = reactive({input$month
})

renderPlot({
  ggplot(HO_Perc, aes(x=HO_Perc[,reactive_data()]))+
  theme_classic()+
  geom_histogram(binwidth=10,col="dodgerblue2", fill = "dodgerblue", alpha = .4)+
  labs(x="Percentage of worktime spent in Home Office", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,100,10), labels = paste0(seq(0,100,10), '%')) +
  scale_y_continuous(breaks=seq(0, 900, 150))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14))
  #HO_Perc_shiny()
  
  
})

```
  
  
# Possibility to Work from Home {.tabset .tabset-fade}

## Plots {-}  
```{r Possibility to work from home, include=T, fig.show='hold', out.width = c('50%','50%'), fig.cap="Allowed to work from home"}
# 1 = Not possible, 2 = Possible
HO_Pos_T3 = round(data.frame(
                    pre = c(length(which(data_HO$T3_HO1 == 2)),
                            length(which(data_HO$T3_HO1 == 1 ))) /length(which((data_HO$T3_HO1 != "NA"))),
                    post = c(length(which(data_HO$T3_HO4 == 2)),
                             length(which(data_HO$T3_HO4 == 1 ))) /length(which((data_HO$T3_HO4 != "NA")))
                       )*100,digits = 2)

HO_Pos_T3 <- HO_Pos_T3 %>%
  mutate(ypos_pre = cumsum(pre)- 0.5*pre) %>% #Positions for the labels inside the Pie-Chart
  mutate(ypos_post = cumsum(post)- 0.5*post)
HO_Pos_T3$labels = c("Yes","No")

  

HO_Pos_pre = ggplot(HO_Pos_T3, aes(x="", y= pre, fill = labels)) +
  geom_bar(width = 1, stat = "identity", color = "white", alpha = .9) +
  scale_fill_discrete(breaks=c("Yes","No")) +
  scale_fill_manual(values = c("#3182bd","#bdd7e7"))+
  coord_polar("y")+
  geom_text(aes(y = ypos_pre, label = paste0(pre, '%')), size=6, colour = "#3e3f3a") +
  guides(fill=guide_legend(title="Before the Pandemic", title.position = "top"))+
  theme_void()+
  theme(legend.position="bottom", legend.text = element_text(size = 14), legend.title = element_text(size = 14.5) )+
  font_colour
  

HO_Pos_pre

HO_Pos_post = ggplot(HO_Pos_T3, aes(x="", y= post, fill = labels)) +
  geom_bar(width = 1, stat = "identity", color = "white", alpha = .9) +
  scale_fill_manual(values = c("#3182bd","#bdd7e7"))+
  coord_polar("y")+
  geom_text(aes(y = ypos_post, label = paste0(post, '%')), size=6, colour = "#3e3f3a") +
  guides(fill=guide_legend(title="Since March", title.position = "top"))+
  theme_void()+
  theme(legend.position="bottom", legend.text = element_text(size = 14), legend.title = element_text(size = 14.5))+
  font_colour

HO_Pos_post

```
  
&nbsp;  
&nbsp;  
 
## Additional Information {-}  
  
One important aspect when talking about Home Office is the extend, to which employers __allow__ their employees to work from home. A manager could have many reasons not to give that permission, such as fearing loss of control over subordinates, thinking that work won't be done in time, doubts about feasibility or just personal preference. Looking at how the constraint of the pandemic and the measures undertaken by the German government influenced the permission of employers might give an insight into how sound those arguments against Home Office really were.  
  
__In March 2020__ the coronavirus hit Germany. Many businesses had to shut down, public life was reduced to a bare minimum. In __April__, we asked our participants two questions:  
  
___"Before the COVID-19 Pandemic (Corona-Crisis): In general, did You have the possibility to work in Home Office?"___  
___"During the past 4 weeks (Since the beginning of March): In general, did You have the possibility to work in Home Office?"___

```{r Possibility to work from home 2, include=T, fig.show='hold', out.width = c('50%','50%'), fig.cap="Allowed to work from home", cache.whatever= list(HO_Pos_pre, HO_Pos_post)}
## For details on the code for the plots, please change to the "Plots"-Tab and unfold the code there. ##

HO_Pos_pre

HO_Pos_post


```
  

# {.unnumbered .toc-ignore}

## Permission over Time {.tabset .tabset-fade}
### Plot {-}  
```{r Permission over Time, include = TRUE, out.width = '100%', fig.height= 3,cache.whatever=months_compl}
HO_Perm = data_HO[,c("ID",grep("_HO4",names(data_HO), value = T))]


HO_Perm_rel = data.frame(
  matrix(
    NA,
    nrow = length(months_compl),
    ncol = 3,
    dimnames = list(c(),c("month","perm", "missing"))
  )
)
HO_Perm_rel$month = as.factor(months_compl)

for (i in 1:length(months_compl)) {
  #means
  if (HO_Perm_rel[i,1] %in% months_miss) {
    HO_Perm_rel[i,2] = round(prop.table(table(HO_Perm[,paste0("T",i+2,"_HO4")]))[2]*100, digits = 2)
  } 
}


for (i in 1:length(months_compl)) {
  #missing mean
  if (HO_Perm_rel[i,1] %in% c("May '20","July '20")) {
    HO_Perm_rel[i,3] = HO_Perm_rel[i,2]
    
  } else if (HO_Perm_rel[i,1] == "June '20"){
    HO_Perm_rel[i,3] = mean(c(HO_Perm_rel[i-1,2],HO_Perm_rel[i+1,2]))
    
  } 
}


HO_Perm_plot = ggplot(HO_Perm_rel, aes(x=month, y = perm)) + 
  geom_line(aes(group=1, color = "#3182bd"), col= "#3182bd", size = 1.5)+
  geom_line(aes(x=month, y=missing, group =1,color = "#3182bd"), col= "#3182bd", size = 1.5, linetype = "dashed" )+
  geom_point(col= "#3182bd", size = 3)+
  geom_area(aes(group=1), fill="#3182bd", alpha=0.4) +
  coord_cartesian(ylim = c(20,60))+
  theme_minimal()+
  scale_x_discrete(limits = months_compl, name ="" )+
  scale_y_continuous(breaks = seq(20,60,10), labels = paste0(seq(20,60,10), "%"), name = "Allowed to work from home")+
  labs(caption = "Note: Data was missing for June.")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  font_colour

HO_Perm_plot


# HO_Perm_rel = data.frame(
#   month = as.factor(months_compl),
#   perm = round(c(
#            (length(which(HO_Perm$T3_HO4 == 2))/length(which((HO_Perm$T3_HO4 != "NA")))),
#            (length(which(HO_Perm$T4_HO4 == 2))/length(which((HO_Perm$T4_HO4 != "NA")))),
#            NA,
#            (length(which(HO_Perm$T6_HO4 == 2))/length(which((HO_Perm$T6_HO4 != "NA")))),
#            (length(which(HO_Perm$T7_HO4 == 2))/length(which((HO_Perm$T7_HO4 != "NA")))),
#            (length(which(HO_Perm$T8_HO4 == 2))/length(which((HO_Perm$T8_HO4 != "NA")))),
#            (length(which(HO_Perm$T9_HO4 == 2))/length(which((HO_Perm$T9_HO4 != "NA")))),
#            (length(which(HO_Perm$T10_HO4 == 2))/length(which((HO_Perm$T10_HO4 != "NA")))),
#            (length(which(HO_Perm$T11_HO4 == 2))/length(which((HO_Perm$T11_HO4 != "NA")))),
#            (length(which(HO_Perm$T12_HO4 == 2))/length(which((HO_Perm$T12_HO4 != "NA"))))
#     
#             )*100, digits = 2)
# )
# 
# # (length(which(HO_Perm$T3_HO4 == 2)) returns the length of the vector of rows, where T3_HO4 is 2 (i.e. those who had permission to work from home). the second term in the division indicates the total amount of responses in the respective month. Rounding all of this after multiplying by 100 for percentages
# 
# HO_Perm_rel$missing = c(NA,
#                         HO_Perm_rel[2,2],
#                         mean(c(HO_Perm_rel[2,2],HO_Perm_rel[4,2])),
#                         HO_Perm_rel[4,2],
#                         NA,
#                         NA,
#                         NA,
#                         NA,
#                         NA,
#                         NA)

```
  
&nbsp;  
&nbsp;  
  
### Additional Information {-}  

Since __June__ life in Germany started gradually coming back to a new __normality__. Businesses were allowed to reopen, albeit under strict regulations and with individual concepts for how to uphold these regulations (so called "hygiene  concepts"). Regarding the previous graphs it becomes obvious, that __before the pandemic__, only __few__ people could __work from home__, but when it became inevitable, the possibility suddenly emerged in many cases, raising questions about why it was not possible before.  
It would be interesting to see, how this general permission fares over time:  

```{r Permission over Time 2, include = TRUE, out.width = '100%', fig.height= 3, cache.whatever= HO_Perm_plot}
## For details on the code for the plots, please change to the "Plots"-Tab and unfold the code there. ##

HO_Perm_plot


```
  
  
Comparable to the first section of this website, the __possibility__ to work from home __peaked in May__ and __steadily declined until September__ after that, showing that in some cases, the workers were given this permission only as long as it was imperative by law or public pressure. Notably, the level is still far from the 22% it was before the pandemic. Furthermore, there is now a coordinated effort by the German _Federal Minister for Labour and Social Affairs_ [Hubertus Heil](https://en.wikipedia.org/wiki/Hubertus_Heil) to __pass legislation__ introducing the "right to Home Office". Regardless of its success in parliament, it illustrates how the topic of Home Office and the possibility to work there gained traction through the pandemic.  

## {-}
***  
  
  
  
# Working from Home - but Where? {.tabset .tabset-fade}  

## Plot {-}  

```{r Location of work, include=TRUE, out.width='100%', fig.height= 3, cache.whatever = months_miss}
# 1 = own, separated Room
# 2 = Designated spot elsewhere
# 3 = Changing places at home depending on the need
# 6 = Other:
# 0 = Missing

HO_loc = data_HO[,grep("_HO18",names(data_HO), value = T )]

HO_loc_prop = data.frame(
  matrix(
    NA,
    ncol = length(months_miss)+1,
    nrow = 4,
    dimnames = list(c(),c("location", months_miss))
  )
)

HO_loc_prop$location = as.factor(c("Own Room","Designated Spot","Changing","Other"))

for (i in 1:(length(months_miss))) {
  HO_loc_prop[,i+1] = prop.table(table(HO_loc[HO_loc[,i] >0,i]))
}




HO_loc_prop_long = gather(HO_loc_prop, month, percentage, -location)
HO_loc_prop_long$month = factor(HO_loc_prop_long$month, labels = months_miss)
HO_loc_prop_long$month_rev = factor(HO_loc_prop_long$month, levels = rev(months_miss))
# here we use rev(), so that the plot returns the months from oldest to most recent

HO_loc_prop_long$location_rev = factor(HO_loc_prop_long$location, levels = rev(c("Own Room","Designated Spot","Changing","Other")))
# for better order

# Not much change over Time
HO_loc_plot = ggplot(HO_loc_prop_long, aes(x=percentage, y = month_rev)) +
  geom_bar(aes(fill = location_rev), stat = "identity")+
  scale_fill_brewer(palette="Blues", direction = 1)+
  theme_minimal()+
  labs(y="", x = "")+
  scale_x_continuous(breaks = seq(0,1,.25), labels = paste0(seq(0,100,25), "%"))+
  guides(fill=guide_legend(title="Workplace in the Home Office", title.position = "top", reverse = T))+
  theme(legend.position="top")+
  font_colour
  

HO_loc_plot


# HO_loc_prop <- data.frame(
#     location = c("Own Room","Designated Spot","Changing","Other"),
#     April = plyr::count(df = HO_loc, vars = "T3_HO18")[2:5,2]/length(which(HO_loc$T3_HO18 > 0)),
#     May = plyr::count(df = HO_loc, vars = "T4_HO18")[2:5,2]/length(which(HO_loc$T4_HO18 > 0)),
#     July = plyr::count(df = HO_loc, vars = "T6_HO18")[2:5,2]/length(which(HO_loc$T6_HO18 > 0)),
#     August = plyr::count(df = HO_loc, vars = "T7_HO18")[2:5,2]/length(which(HO_loc$T7_HO18 > 0)),
#     September = plyr::count(df = HO_loc, vars = "T8_HO18")[2:5,2]/length(which(HO_loc$T8_HO18 > 0)),
#     October = plyr::count(df = HO_loc, vars = "T9_HO18")[2:5,2]/length(which(HO_loc$T9_HO18 > 0)),
#     November = plyr::count(df = HO_loc, vars = "T10_HO18")[2:5,2]/length(which(HO_loc$T10_HO18 > 0)),
#     December = plyr::count(df = HO_loc, vars = "T11_HO18")[2:5,2]/length(which(HO_loc$T11_HO18 > 0)),
#     January = plyr::count(df = HO_loc, vars = "T12_HO18")[2:5,2]/length(which(HO_loc$T12_HO18 > 0))
#     )
# # this one is a bit complicated :D I wanted to have the proportions of people woking from the respective places.
# # plyr::count(df = HO_loc, vars = "T3_HO18") counts the frequency of every value inside a vector and returns a tibble with two columns (Value and Frequency) per variable. in this case, there are 6 "Values", being 0,1,2,3,6 and NA.
# # by adding [2:5,2] we say that we want only the frequencies (second column) of 1,2,3 and 6 (rows 2:5), since these are the ones that are interesting for us. (see avove)
# # length(which(HO_loc$T3_HO18 > 0)) returns the total of valid responses

```
  
&nbsp;  
&nbsp;  
  
## Additional Information {-}  

Home Office does not equal Home Office. There is a difference in one's experience when working from home, depending on the __locality__. Some people have the opportunity of a __separate room__, which is reserved for work only and has all the needed equipment and supplies, while others might need to __improvise a workspace__, especially if they never worked from home before. No matter how it is done, there needs to be a separate place at home, where one can and must work. This is important in terms of __detachment and productivity__. The local separation of work and leisure, typically provided by an outside workplace, helps to separate work and leisure mentally, which in turn increases attention, concentration and motivation.  
In our sample, we asked our participants ___where they worked from when in Home Office___. One could expect to see an increase in designated spots as time progresses and people have had the chance to accommodate themselves to working from home. Unfortunately, this trend couldn't be identified in our data:

```{r Location of work 2, include=TRUE, out.width='100%', fig.height= 3, cache.whatever= HO_loc_plot}
## For details on the code for the plots, please change to the "Plots"-Tab and unfold the code there. ##

HO_loc_plot

```
  
Even though there was __no noteworthy change over time__, the aspect of locality at home should __not be dismissed__ too early. While further analyses would go beyond the scope of this brief discussion, one could still wonder about possible associated effects. Is there a relationship between place of work and satisfaction? If yes, which one would be the most appropriate? Is a designated spot enough, or does having an own room add incremental gain in satisfaction?
  
***  
  
  
  
# Feeling of Isolation {.tabset .tabset-fade}  

## Plot {-}  

```{r Isolation, include = TRUE, out.width='100%', fig.height=3.5, cache.whatever=months_miss}
# HO13 - 16
HO_Isol_Vars = c(grep("_HO13", names(data_HO), value = T), grep("_HO14", names(data_HO), value = T),grep("_HO15", names(data_HO), value = T),grep("_HO16", names(data_HO), value = T))


HO_Isol = data_HO[, c("ID", HO_Isol_Vars)]
# compiling individual means
for (i in 1:length(months_miss)) {
  if (i %in% c(1,2)) {
    HO_Isol[,paste0("T",i+2,"mean")] = rowMeans(HO_Isol[,grep(paste0("T",i+2,"_HO1"), names(HO_Isol), value = T)])
  } else {
    HO_Isol[,paste0("T",i+3,"mean")] = rowMeans(HO_Isol[,grep(paste0("T",i+3,"_HO1"), names(HO_Isol), value = T)])
  }
}


HO_Isol_means = data.frame(
  matrix(
    NA,
    ncol = 5,
    nrow = length(months_compl),
    dimnames = list(c(),c("month","means","sd","missing","sd_missing"))
  )
)

HO_Isol_means$month = as.factor(months_compl)

for (i in 1:length(months_compl)) {
  #means
  if (HO_Isol_means[i,1] %in% months_miss) {
    HO_Isol_means[i,2] = mean(HO_Isol[,paste0("T",i+2,"mean")], na.rm = T)
  } 
  
  #sds
  if (HO_Isol_means[i,1] %in% months_miss) {
    HO_Isol_means[i,3] = sd(HO_Isol[,paste0("T",i+2,"mean")], na.rm = T)
  } 
}


for (i in 1:length(months_compl)) {
  #missing mean
  if (HO_Isol_means[i,1] %in% c("May '20","July '20")) {
    HO_Isol_means[i,4] = HO_Isol_means[i,2]
    
  } else if (HO_Isol_means[i,1] == "June '20"){
    HO_Isol_means[i,4] = mean(c(HO_Isol_means[i-1,2],HO_Isol_means[i+1,2]))
    
  } 
  
  #missing sd
  if (HO_Isol_means[i,1] %in% c("May '20","July '20")) {
    HO_Isol_means[i,5] = HO_Isol_means[i,3]
    
  } else if (HO_Isol_means[i,1] == "June '20"){
    HO_Isol_means[i,5] = mean(c(HO_Isol_means[i-1,3],HO_Isol_means[i+1,3]))
    
  } 
}


HO_Isol_plot = ggplot(HO_Isol_means, aes(x=month, y = means)) + 
  geom_line(aes(group=1, color = "#3182bd"), col= "#3182bd", size = 1.5)+
  geom_line(aes(x=month, y=missing, group =1,color = "#3182bd"), col= "#3182bd", size = 1.5, linetype = "dashed" )+
  geom_point(col= "#3182bd", size = 3)+
  geom_ribbon(aes(y=means, ymin = means - (sd/2), ymax = means + (sd/2), group = 1),fill="#3182bd", alpha=0.4) +
  geom_ribbon(aes(y=missing, ymin = missing - (sd_missing/2), ymax = missing + (sd_missing/2), group = 1),fill="#3182bd", alpha=0.3) +
  theme_minimal()+
  coord_cartesian(ylim = c(1,3))+
  scale_x_discrete(limits = months_compl, name ="" )+
  scale_y_continuous(breaks = seq(1.5,3,0.5), name = "Feeling of Isolation")+
  labs(caption = "Note: Data was missing for June. Ribbon represents 1SD around the mean.")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  font_colour

HO_Isol_plot

HO_Isol =  cbind(HO_Isol, HO_Perc)
#adding percentage of time worked in Home Office for Correlation seen in the text below
HO_Isol_Perc_Cor = c(1:length(months_miss))
HO_Isol_Perc_Cor[] = NA

for (i in 1:length(months_miss)) {
  if (i < 3) {
    HO_Isol_Perc_Cor[i] = cor(HO_Isol[,paste0("T",i+2,"mean")], HO_Isol[,paste0("T",i+2,"_HO6")], use = "complete.obs")
  } else {
    HO_Isol_Perc_Cor[i] = cor(HO_Isol[,paste0("T",i+3,"mean")], HO_Isol[,paste0("T",i+3,"_HO6")], use = "complete.obs")
  }
  
}
mean_r =round(mean(HO_Isol_Perc_Cor), digits = 2)



# HO_Isol$T3mean = rowMeans(HO_Isol[,grep("T3_HO1", names(HO_Isol), value = T)])
# HO_Isol$T4mean = rowMeans(HO_Isol[,grep("T4_HO1", names(HO_Isol), value = T)])
# HO_Isol$T6mean = rowMeans(HO_Isol[,grep("T6_HO1", names(HO_Isol), value = T)])
# HO_Isol$T7mean = rowMeans(HO_Isol[,grep("T7_HO1", names(HO_Isol), value = T)])
# HO_Isol$T8mean = rowMeans(HO_Isol[,grep("T8_HO1", names(HO_Isol), value = T)])
# HO_Isol$T9mean = rowMeans(HO_Isol[,grep("T9_HO1", names(HO_Isol), value = T)])
# HO_Isol$T10mean = rowMeans(HO_Isol[,grep("T10_HO1", names(HO_Isol), value = T)])
# HO_Isol$T11mean = rowMeans(HO_Isol[,grep("T11_HO1", names(HO_Isol), value = T)])
# HO_Isol$T12mean = rowMeans(HO_Isol[,grep("T12_HO1", names(HO_Isol), value = T)])
# # Compiling the respective individual means of Isolation at every datapoint (dyplr might have given an easyer way)

# HO_Isol_means = data.frame(
#   month = as.factor(months_compl),
#   means = c(
#     mean(HO_Isol$T3mean, na.rm = T),
#     mean(HO_Isol$T4mean, na.rm = T),
#     NA,
#     mean(HO_Isol$T6mean, na.rm = T),
#     mean(HO_Isol$T7mean, na.rm = T),
#     mean(HO_Isol$T8mean, na.rm = T),
#     mean(HO_Isol$T9mean, na.rm = T),
#     mean(HO_Isol$T10mean, na.rm = T),
#     mean(HO_Isol$T11mean, na.rm = T),
#     mean(HO_Isol$T12mean, na.rm = T)
#   ),
#   missing = c(
#     NA,
#     mean(HO_Isol$T4mean, na.rm = T),
#     mean(c(mean(HO_Isol$T4mean, na.rm = T),mean(HO_Isol$T6mean, na.rm = T))),
#     mean(HO_Isol$T6mean, na.rm = T),
#     NA,
#     NA,
#     NA,
#     NA,
#     NA,
#     NA
#   ),
#   sd = c(
#     sd(HO_Isol$T3mean, na.rm = T),
#     sd(HO_Isol$T4mean, na.rm = T),
#     NA,
#     sd(HO_Isol$T6mean, na.rm = T),
#     sd(HO_Isol$T7mean, na.rm = T),
#     sd(HO_Isol$T8mean, na.rm = T),
#     sd(HO_Isol$T9mean, na.rm = T),
#     sd(HO_Isol$T10mean, na.rm = T),
#     sd(HO_Isol$T11mean, na.rm = T),
#     sd(HO_Isol$T12mean, na.rm = T)
#   ),
#   sd_missing = c(
#     NA,
#     sd(HO_Isol$T4mean, na.rm = T),
#     mean(c(sd(HO_Isol$T4mean, na.rm = T), sd(HO_Isol$T6mean, na.rm = T))),
#     sd(HO_Isol$T6mean, na.rm = T),
#     NA,
#     NA,
#     NA,
#     NA,
#     NA,
#     NA
#   )
#     
# )
# 

# mean_r = round(mean(c(
#   cor(HO_Isol[,"T3mean"], HO_Isol[,"T3_HO6"], use = "complete.obs"),
#   cor(HO_Isol[,"T4mean"], HO_Isol[,"T4_HO6"], use = "complete.obs"),
#   cor(HO_Isol[,"T6mean"], HO_Isol[,"T6_HO6"], use = "complete.obs"),
#   cor(HO_Isol[,"T7mean"], HO_Isol[,"T7_HO6"], use = "complete.obs"),
#   cor(HO_Isol[,"T8mean"], HO_Isol[,"T8_HO6"], use = "complete.obs"),
#   cor(HO_Isol[,"T9mean"], HO_Isol[,"T9_HO6"], use = "complete.obs"),
#   cor(HO_Isol[,"T10mean"], HO_Isol[,"T10_HO6"], use = "complete.obs"),
#   cor(HO_Isol[,"T11mean"], HO_Isol[,"T11_HO6"], use = "complete.obs"),
#   cor(HO_Isol[,"T12mean"], HO_Isol[,"T12_HO6"], use = "complete.obs")
# )), digits = 2)

```
  
&nbsp;  
&nbsp;  
  
## Additional Information {-}

In most cases, working is a social process and the workplace is an inherently social space. Regular meetings, quick coordination of further steps, running into each other in the hallways, eating lunch together, sharing personal stories and experiences, and so on. All of that was not possible in the same manner when a portion of the workforce was forced to work from home only.  
In the field of telework and telecommuting, the concept of __Professional Isolation__ emerged, being defined as __"a state of mind or belief that one is out of touch with others in the workplace"__ [@Golden.2008] (Golden et al., 2008). This isn't necessarily bound to happen when people work from home. In its core, it is a __feeling of not being involved__ in the essential professional networks, which __can also occur__ while sitting __in a regular office__. Nonetheless there is a tendency among teleworkers to lack social comparison of their performance and more complex contextual clues about their workplace.  
In line of this research, we measured professional isolation by having people rate, for example:  
  
_"I feel left out on activities and meetings that could enhance my career"_  
_"I miss informal interaction with others."_
```{r Isolation 2, include = TRUE, out.width='100%', fig.height=3.5, cache.whatever= HO_Isol_plot}
## For details on the code for the plots, please change to the "Plots"-Tab and unfold the code there. ##

HO_Isol_plot

```
Regarding the fact, that the response Scale ranged from 1 - _Never_ to 5 - _Very often_, this level of average Isolation is rather surprising. Apparently, __feeling out of the loop__ and missing the informal conversation with colleagues __wasn't as much of an issue__.  
The potential reasons for that can be manyfold. Maybe the __communication through digital media__ was __sufficient__ to replace real meetings. Or maybe the __data isn't representative__, as not that many people indicated working from home entirely.   
Investigating a smaller subset of participants, the ones who spent most of their worktime in Home Office, could yield different results. The __mean correlation of `r mean_r`__ between the percentage of __time spent in Home Office__ and feeling of __professional isolation__ serves as further evidence of this possibility, as it shows that the more one works from home, the more he or she tends to feel isolated.  

***  
  
  
  
# Satisfaction with Home Office 

## Overall Development over Time {.tabset .tabset-fade}   

### Plot {-}  

&nbsp;  
&nbsp;  
  
```{r Satisfaction, include=TRUE, out.width='100%', fig.height=3.5, cache.whatecer= months_miss}
# HO31 = Satisfaction 
# HO32 = Efficacy
# HO3 = Equipment (1=No, 2=Yes)
# covid11 = Childcare (2 = Emergency Care, 3 = I cared at home, 4 = My Partner cared at home, 5 = other family members/friends, 6 = other)
Sat_variables = c(grep("_HO3",names(data_HO), value = T),grep("_covid11",names(data_HO), value = T), "ID") 
HO_Sat =  data_HO[,Sat_variables]
HO_Sat = HO_Sat[,-which(names(HO_Sat) %in% grep("_HO30",names(HO_Sat), value = T))]
# since grep("_HO3",names(data_HO), value = T) returns all the names with _H03 in them, and we don't need HO30, this line above removes all the Tx_HO30 from the dataframe


# Satisfaction (_HO31) was measured on a scale of 1-5, but there are Missings in the form of zeroes. So in order to avoid a distortion of the mean, we only use the rows, where the value is greater than 0 
HO_Sat_means = data.frame(
  matrix(
    NA,
    ncol = 9,
    nrow = length(months_compl),
    dimnames = list(c(),c("month","means","sd","missing","mis_sd","means_care_self","means_care_partner", "missing_self", "missing_partner"))
  )
)

HO_Sat_means$month = as.factor(months_compl)

for (i in 1:length(months_compl)) {
  #means
  if (HO_Sat_means[i,1] %in% months_miss) {
    HO_Sat_means[i,2] = mean(HO_Sat[HO_Sat[,paste0("T",i+2,"_HO31")]>0,paste0("T",i+2,"_HO31")], na.rm = T)
  } 

  #sds
  if (HO_Sat_means[i,1] %in% months_miss) {
    HO_Sat_means[i,3] = sd(HO_Sat[HO_Sat[,paste0("T",i+2,"_HO31")]>0,paste0("T",i+2,"_HO31")], na.rm = T)
  } 
}


for (i in 1:length(months_compl)) {
  #missing mean
  if (HO_Sat_means[i,1] %in% c("May '20","July '20")) {
    HO_Sat_means[i,4] = HO_Sat_means[i,2]
    
  } else if (HO_Sat_means[i,1] == "June '20"){
    HO_Sat_means[i,4] = mean(c(HO_Sat_means[i-1,2],HO_Sat_means[i+1,2]))
    
  } 
  
  #missing sd
  if (HO_Sat_means[i,1] %in% c("May '20","July '20")) {
    HO_Sat_means[i,5] = HO_Sat_means[i,3]
    
  } else if (HO_Sat_means[i,1] == "June '20"){
    HO_Sat_means[i,5] = mean(c(HO_Sat_means[i-1,3],HO_Sat_means[i+1,3]))
    
  } 
}


HO_Sat_plot = ggplot(HO_Sat_means, aes(x=month, y = means)) + 
  geom_line(aes(group=1, color = "#3182bd"), col= "#3182bd", size = 1.5)+
  geom_line(aes(x=month, y=missing, group =1,color = "#3182bd"), col= "#3182bd", size = 1.5, linetype = "dashed" )+
  geom_point(col= "#3182bd", size = 3)+
  geom_ribbon(aes(y=means, ymin = means - (sd/2), ymax = means + (sd/2), group = 1),fill="#3182bd", alpha=0.4) +
  geom_ribbon(aes(y=missing, ymin = missing - (mis_sd/2), ymax = missing + (mis_sd/2), group = 1),fill="#3182bd", alpha=0.3) +
  theme_minimal()+
  coord_cartesian(ylim = c(1,5))+
  scale_x_discrete(limits = months_compl, name ="" )+
  scale_y_continuous(breaks = seq(1,5,1), name = "Satisfaction with Home Office")+
  labs(caption = "Note: Data was missing for June. Ribbon represents 1SD around the mean.")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  font_colour
HO_Sat_plot

# Old Code
#  HO_Sat_means = data.frame(
#   month = as.factor(months_compl[1:10]),
#   means = c(
#     mean(HO_Sat[HO_Sat$T3_HO31>0,"T3_HO31"], na.rm = T),
#     mean(HO_Sat[HO_Sat$T4_HO31>0,"T4_HO31"], na.rm = T),
#     NA,
#     mean(HO_Sat[HO_Sat$T6_HO31>0,"T6_HO31"], na.rm = T),
#     mean(HO_Sat[HO_Sat$T7_HO31>0,"T7_HO31"], na.rm = T),
#     mean(HO_Sat[HO_Sat$T8_HO31>0,"T8_HO31"], na.rm = T),
#     mean(HO_Sat[HO_Sat$T9_HO31>0,"T9_HO31"], na.rm = T),
#     mean(HO_Sat[HO_Sat$T10_HO31>0,"T10_HO31"], na.rm = T),
#     mean(HO_Sat[HO_Sat$T11_HO31>0,"T11_HO31"], na.rm = T),
#     mean(HO_Sat[HO_Sat$T12_HO31>0,"T12_HO31"], na.rm = T)
#     ),
#   sd = c(
#     sd(HO_Sat[HO_Sat$T3_HO31>0,"T3_HO31"], na.rm = T),
#     sd(HO_Sat[HO_Sat$T4_HO31>0,"T4_HO31"], na.rm = T),
#     NA,
#     sd(HO_Sat[HO_Sat$T6_HO31>0,"T6_HO31"], na.rm = T),
#     sd(HO_Sat[HO_Sat$T7_HO31>0,"T7_HO31"], na.rm = T),
#     sd(HO_Sat[HO_Sat$T8_HO31>0,"T8_HO31"], na.rm = T),
#     sd(HO_Sat[HO_Sat$T9_HO31>0,"T9_HO31"], na.rm = T),
#     sd(HO_Sat[HO_Sat$T10_HO31>0,"T10_HO31"], na.rm = T),
#     sd(HO_Sat[HO_Sat$T11_HO31>0,"T11_HO31"], na.rm = T),
#     sd(HO_Sat[HO_Sat$T12_HO31>0,"T12_HO31"], na.rm = T)
#   ),
#   missing = c(
#     NA,
#     mean(HO_Sat[HO_Sat$T4_HO31>0,"T4_HO31"], na.rm = T),
#     mean(c(mean(HO_Sat[HO_Sat$T4_HO31>0,"T4_HO31"], na.rm = T),mean(HO_Sat[HO_Sat$T6_HO31>0,"T6_HO31"], na.rm = T))),
#     mean(HO_Sat[HO_Sat$T6_HO31>0,"T6_HO31"], na.rm = T),
#     NA,
#     NA,
#     NA,
#     NA,
#     NA,
#     NA
#   ),
#   mis_sd = c(
#      NA,
#     sd(HO_Sat[HO_Sat$T4_HO31>0,"T4_HO31"], na.rm = T),
#     mean(c(sd(HO_Sat[HO_Sat$T4_HO31>0,"T4_HO31"], na.rm = T),sd(HO_Sat[HO_Sat$T6_HO31>0,"T6_HO31"], na.rm = T))),
#     sd(HO_Sat[HO_Sat$T6_HO31>0,"T6_HO31"], na.rm = T),
#     NA,
#     NA,
#     NA,
#     NA,
#     NA,
#     NA
#   )
# )

```
 

### Additional Information {-}   
At the end of the day, one of the most important lesson to draw from this pandemic regarding Home Office would be how to make working from home as __satisfactory__ as possible. To be able to draw conclusions from this data, it is necessary to first get an __overall view of the satisfaction__ experienced when it comes to working from home, and subsequently look at potential correlates and causes.  


```{r Satisfaction 2, include=TRUE, out.width='100%', fig.height=3.5, cache.whatever= HO_Sat_plot}
## For details on the code for the plots, please change to the "Plots"-Tab and unfold the code there. ##

HO_Sat_plot
```
  
Satisfaction was __consistently above the average of 3__, indicating that most people were __rather happy__ with their overall experience in Home Office.   
Now that in and of itself is good news. Even though the all-encompassing situation was rather grim, people apparently were more or less happy with their work from home. The interesting point now is to find out, __what caused__ this satisfaction, so that we can learn how to improve the experience for others.
  
## Child Care {.tabset .tabset-fade}  

### Plot {-}

```{r Satisfaction parenting, include= TRUE, out.width='100%', fig.height=3.5, cache.whatecer= months_miss}

# Here we use the syntax of dplyr. We add a column with the means of "satisfaction" by group (Childcare provided by oneself, covid11 == 3, or by the partner, covid11 == 4) by using the "mutate" function: creating a vector called means_care_..., filling it with the conditional means, and adding it to the existing dataframe.

for (i in 1:length(months_compl)) {
  #means for childcare provided by oneself
  if (HO_Sat_means[i,1] %in% months_miss) {
    HO_Sat_means[i,6] = mean(
      HO_Sat[
        (HO_Sat[,paste0("T",i+2,"_HO31")]>0 & HO_Sat[,paste0("T",i+2,"_covid11")]==3),
        paste0("T",i+2,"_HO31")], 
      na.rm = T
      )
    # Means for childcare provided by partner
    HO_Sat_means[i,7] = mean(
      HO_Sat[
        (HO_Sat[,paste0("T",i+2,"_HO31")]>0 & HO_Sat[,paste0("T",i+2,"_covid11")]==4),
        paste0("T",i+2,"_HO31")], 
      na.rm = T
      )
  } 
  
}


for (i in 1:length(months_compl)) {
  
  if (HO_Sat_means[i,1] %in% c("May '20","July '20")) {
    #missing mean self
    HO_Sat_means[i,8] = HO_Sat_means[i,6]
    #missing mean partner
    HO_Sat_means[i,9] = HO_Sat_means[i,7]
    
  } else if (HO_Sat_means[i,1] == "June '20"){
    #missing mean self
    HO_Sat_means[i,8] = mean(c(HO_Sat_means[i-1,6],HO_Sat_means[i+1,6]))
    #missing mean partner
    HO_Sat_means[i,9] = mean(c(HO_Sat_means[i-1,7],HO_Sat_means[i+1,7]))
  } 
  
}



colors = c("oneself" = "#e6550d", "partner" = "#31a354")
# this is for the subsequent plot, in Order to have a legend with custom labels

HO_Sat_care_plot = ggplot(HO_Sat_means, aes(x=month, y = means)) + 
  geom_line(aes(group=1, color = "#3182bd"),col = "#3182bd", size = 1, linetype = "twodash")+
  geom_line(aes(x=month, y=missing, group =1,color = "#3182bd"), col = "#3182bd", size = 1, linetype = "dashed" )+
  geom_point(color= "#3182bd", size = 1.5)+
  geom_ribbon(aes(y=means, ymin = means - (sd/2), ymax = means + (sd/2), group = 1),fill="#3182bd", alpha=0.4) +
  geom_ribbon(aes(y=missing, ymin = missing - (mis_sd/2), ymax = missing + (mis_sd/2), group = 1),fill="#3182bd", alpha=0.3) +
  theme_minimal()+
  coord_cartesian(ylim = c(1,5))+
  scale_x_discrete(limits = months_compl, name ="" )+
  scale_y_continuous(breaks = seq(1,5,1), name = "Satisfaction with Home Office")+
  labs(caption = "Note: Data was missing for June. Ribbon represents 1SD around the mean.", color = "Childcare provided by...")+
  
  # up until now, same graph as before. Adding the conditional lines:
  
  geom_line(aes(x=month, y= means_care_self, group=1, color="oneself"), size = 1.5 )+
  geom_line(aes(x=month, y=missing_self, group =1,color = "oneself"),  size = 1.5, linetype = "dashed" )+
  geom_point(aes(x=month, y = means_care_self, color = "oneself"), size = 3)+
  
  geom_line(aes(x=month, y= means_care_partner, group=1, color="partner"), size = 1.5 )+
  geom_line(aes(x=month, y=missing_partner, group =1,color = "partner"), size = 1.5, linetype = "dashed" )+
  geom_point(aes(x=month, y = means_care_partner, color = "partner"), size = 3)+
  
  #we defined the colors above, so we can use color = "oneself"/"partner" 
  
  scale_color_manual(values = colors)+
  # Here we tell the legend, how it should call its values, using the vector from above
  
  theme(legend.position = "top")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  font_colour

HO_Sat_care_plot

# Old code
# HO_Sat_means = HO_Sat_means %>%
#   mutate(means_care_self = c(
#     mean(HO_Sat[(HO_Sat$T3_covid11 == 3 & HO_Sat$T3_HO31>0), "T3_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T4_covid11 == 3 & HO_Sat$T4_HO31>0), "T4_HO31"], na.rm = T),
#     NA,
#     mean(HO_Sat[(HO_Sat$T6_covid11 == 3 & HO_Sat$T6_HO31>0), "T6_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T7_covid11 == 3 & HO_Sat$T7_HO31>0), "T7_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T8_covid11 == 3 & HO_Sat$T8_HO31>0), "T8_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T9_covid11 == 3 & HO_Sat$T9_HO31>0), "T9_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T10_covid11 == 3 & HO_Sat$T10_HO31>0), "T10_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T11_covid11 == 3 & HO_Sat$T11_HO31>0), "T11_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T12_covid11 == 3 & HO_Sat$T12_HO31>0), "T12_HO31"], na.rm = T)
#   ))%>%
#   mutate(means_care_partner =  c(
#     mean(HO_Sat[(HO_Sat$T3_covid11 == 4 & HO_Sat$T3_HO31>0), "T3_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T4_covid11 == 4 & HO_Sat$T4_HO31>0), "T4_HO31"], na.rm = T),
#     NA,
#     mean(HO_Sat[(HO_Sat$T6_covid11 == 4 & HO_Sat$T6_HO31>0), "T6_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T7_covid11 == 4 & HO_Sat$T7_HO31>0), "T7_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T8_covid11 == 4 & HO_Sat$T8_HO31>0), "T8_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T9_covid11 == 4 & HO_Sat$T9_HO31>0), "T9_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T10_covid11 == 4 & HO_Sat$T10_HO31>0), "T10_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T11_covid11 == 4 & HO_Sat$T11_HO31>0), "T11_HO31"], na.rm = T),
#     mean(HO_Sat[(HO_Sat$T12_covid11 == 4 & HO_Sat$T12_HO31>0), "T12_HO31"], na.rm = T)
#   ))%>%
#   mutate(missing_self = c(
#     NA,
#      mean(HO_Sat[(HO_Sat$T4_covid11 == 3 & HO_Sat$T4_HO31>0), "T4_HO31"], na.rm = T),
#     mean(c( mean(HO_Sat[(HO_Sat$T4_covid11 == 3 & HO_Sat$T4_HO31>0), "T4_HO31"], na.rm = T),mean(HO_Sat[(HO_Sat$T6_covid11 == 3 & HO_Sat$T6_HO31>0), "T6_HO31"], na.rm = T))),
#     mean(HO_Sat[(HO_Sat$T6_covid11 == 3 & HO_Sat$T6_HO31>0), "T6_HO31"], na.rm = T),
#     NA,
#     NA,
#     NA,
#     NA,
#     NA,
#     NA
#   ))%>%
#   mutate(missing_partner = c(
#     NA,
#     mean(HO_Sat[(HO_Sat$T4_covid11 == 4 & HO_Sat$T4_HO31>0), "T4_HO31"], na.rm = T),
#     mean(c( mean(HO_Sat[(HO_Sat$T4_covid11 == 4 & HO_Sat$T4_HO31>0), "T4_HO31"], na.rm = T),mean(HO_Sat[(HO_Sat$T6_covid11 == 4 & HO_Sat$T6_HO31>0), "T6_HO31"], na.rm = T))),
#     mean(HO_Sat[(HO_Sat$T6_covid11 == 4 & HO_Sat$T6_HO31>0), "T6_HO31"], na.rm = T),
#     NA,
#     NA,
#     NA,
#     NA,
#     NA,
#     NA
#   ))
```
  
&nbsp;  
&nbsp;  
  
### Additional Information {-}
One factor that could hold influence is higher demand at work, like is generally theorized in the __Work-Demands-Resources-Model__. One such demand could be the additional __workload of caring for children__, since kindergartens and schools were closed also and only in extreme cases parents could get "emergency childcare". So, let us compare the situation of those, who had to care for their children by themselves with those, whose partners took on the task of caring for their children.  

```{r Satisfaction parenting 2, include= TRUE, out.width='100%', fig.height=3.5, cache.whatever= HO_Sat_care_plot}
## For details on the code for the plots, please change to the "Plots"-Tab and unfold the code there. ##


HO_Sat_care_plot
```

Surprisingly, whether or not one had to care for their children at home had seemingly __no effect__ on the overall satisfaction with Home Office. At least, there is no indication for a main effect. Further down the way, a more complex investigation into corollaries and moderators might, however, uncover clearer effects.  
  
## Efficacy {.tabset .tabset-fade}  

### Plot {-}  

&nbsp;  
&nbsp;
  
```{r efficacy , include= TRUE, fig.height=3.5, out.width='100%', cache.whatecer= months_miss }

# Using the reshape function for long format now
HO_Sat_Eff =   reshape(
  
  HO_Sat[,!(names(HO_Sat) %in% c("T4_HO3","T6_HO3", grep( "_covid11",names(HO_Sat), value = T)))], 
  # Excluding the not needed variables from the dataframe, namely the childcare variables and the equipment variables for T4 and T6
  
  varying = list(grep( "_HO31", names(HO_Sat), value = T), grep("_HO32", names(HO_Sat), value = T)), 
  # Telling reshape, which variables should be compiled into one, here they are HO31 (Satisfaction) and HO32 (Efficacy) respectively
  
  v.names = c("Sat", "Eff"),
  # How should the newly created variables be called?
  
  direction = "long", 
  # Reshape into which direction?
  
  timevar = "month", 
  # How should the variable indicating the timepoint be called?
  
  idvar = "ID" 
  # What's the Variable identifying unique observations?
)               
                       
                    

## test reshape
# These tables can be uncommented and executed, to be sure that the reshaping was successfull. If it was, every one should return only TRUEs
# table(HO_Sat$T3_HO31 == HO_Sat_Eff[HO_Sat_Eff$month==1, "Sat"])
# table(HO_Sat$T4_HO31 == HO_Sat_Eff[HO_Sat_Eff$month==2, "Sat"])
# table(HO_Sat$T6_HO31 == HO_Sat_Eff[HO_Sat_Eff$month==3, "Sat"])
# table(HO_Sat$T7_HO31 == HO_Sat_Eff[HO_Sat_Eff$month==4, "Sat"])
# table(HO_Sat$T8_HO31 == HO_Sat_Eff[HO_Sat_Eff$month==5, "Sat"])
# table(HO_Sat$T9_HO31 == HO_Sat_Eff[HO_Sat_Eff$month==6, "Sat"])
# table(HO_Sat$T10_HO31 == HO_Sat_Eff[HO_Sat_Eff$month==7, "Sat"])
# table(HO_Sat$T11_HO31 == HO_Sat_Eff[HO_Sat_Eff$month==8, "Sat"])
# 
# table(HO_Sat$T3_HO32 == HO_Sat_Eff[HO_Sat_Eff$month==1, "Eff"])
# table(HO_Sat$T4_HO32 == HO_Sat_Eff[HO_Sat_Eff$month==2, "Eff"])
# table(HO_Sat$T6_HO32 == HO_Sat_Eff[HO_Sat_Eff$month==3, "Eff"])
# table(HO_Sat$T7_HO32 == HO_Sat_Eff[HO_Sat_Eff$month==4, "Eff"])
# table(HO_Sat$T8_HO32 == HO_Sat_Eff[HO_Sat_Eff$month==5, "Eff"])
# table(HO_Sat$T9_HO32 == HO_Sat_Eff[HO_Sat_Eff$month==6, "Eff"])
# table(HO_Sat$T10_HO32 == HO_Sat_Eff[HO_Sat_Eff$month==7, "Eff"])
# table(HO_Sat$T11_HO32 == HO_Sat_Eff[HO_Sat_Eff$month==8, "Eff"])

HO_Sat_Eff$month = factor(HO_Sat_Eff$month,
                          labels = months_miss)

HO_Sat_Eff = HO_Sat_Eff[HO_Sat_Eff$Sat > 0 & HO_Sat_Eff$Eff >0,]
# Removing all the missing Values of satisfaction and efficay

r_Sat_Eff = round(cor(HO_Sat_Eff$Sat,HO_Sat_Eff$Eff, use = "complete.obs"), digits = 2)


HO_Sat_Eff_plot = ggplot(HO_Sat_Eff, aes(x=Eff,y= Sat)) + 
  geom_smooth(method = lm, size = 0.5) +
  theme_minimal()+
  coord_cartesian(xlim = c(1,5), ylim = c(1,5))+
  scale_fill_brewer(palette = "Blues")+
  labs(x="Efficacy in Home Office",y = "Satisfaction with Home Office", caption = paste0("Mean correlation over all months was .", 100*r_Sat_Eff), title = "Relationship between efficacy in and satisfaction with Home Office", subtitle = "Over all months")+
  font_colour

HO_Sat_Eff_plot

```
  

### Additional Information {-}
In general, people tend to crave a feeling of __self-efficacy__ - that they can __accomplish goals__ by putting in their own effort. Whether at work, while exercising one's hobbies or in social relationships, __self-efficacy__ - and a lack thereof - plays an integral role in __forming__ one's __self-image__ and __influences well-being__. Therefore, we can assume, that the feeling of self-efficacy also took part in the rating of __satisfaction__ with Home Office. The following graph shows the relationship between these two constructs over all measurement points. Upon first inspection it became obvious, that the coefficients did not vary significantly between the months.  
To measure self-efficacy, we asked our participants to rate the following statement:  
__"I am certain that I can successfully fulfill my tasks in the Home Office."__
```{r efficacy 2, include= TRUE, fig.height=3.5, out.width='100%', cache.whatever= HO_Sat_Eff_plot }
## For details on the code for the plots, please change to the "Plots"-Tab and unfold the code there. ##

HO_Sat_Eff_plot

```
  
  
As predicted, there was a very __strong relationship__ between __satisfaction and efficacy__, further emphasizing the importance of the latter. Nevertheless, this was just a quick and cursory analysis which doesn't allow causal inference yet. A cross-lagged study predicting satisfaction in point _T_ through efficacy at point _T-1_ and vice versa could give further insight into the underlying mechanisms.  
  
## {-}  
  
## Sufficient Equipment {.tabset .tabset-fade}

### Plot {-}  
```{r equipment, include=T, out.extra='style="float:left; padding:10px"', fig.height=5, fig.width=3}

HO_Sat_Eff$Equip_T3 = factor(HO_Sat_Eff$T3_HO3, levels = 0:2, labels = c("Missing","Insufficient", "Sufficient"))
# creating a new factor 


HO_Sat_Equip= 
  dplyr::filter(HO_Sat_Eff,month == "April '20",Equip_T3 != "Missing" ) %>% 
  # Filtering the dataframe to only use the rows, where month == "April" and information about the Equipment is not "Missing" 
  
  dplyr::group_by(Equip_T3) %>%
  # Grouping this filtered dataframe by the levels of Equip_T3, being Sufficient and Insufficient
  
  dplyr::summarise(Sat_mean = mean(Sat),Sat_sd= sd(Sat))
  # Applying multiple functions to the filtered and grouped dataset, namely mean to create Sat_Mean and sd to create Sat_sd


#insufficient, sufficient

HO_Equip = plyr::count(HO_Sat_Eff[HO_Sat_Eff$month == "April '20",], vars = "Equip_T3")[2:3,2]
# Counting, how many people indicated sufficient and insufficient equipment

r_Sat_Equip = round(
  cor(
    filter(HO_Sat_Eff,month == "April '20",Equip_T3 != "Missing" )$Sat, 
    filter(HO_Sat_Eff,month == "April '20",Equip_T3 != "Missing" )$T3_HO3),
  digits = 2)*100
# Correlating satisfaction and equipment for the subtitle below


HO_Sat_Equip_plot = ggplot(HO_Sat_Equip, aes(y= Sat_mean, x = Equip_T3, fill =Equip_T3))+
                    geom_bar(stat = "identity")+
                    geom_errorbar(aes(ymin = Sat_mean - Sat_sd , ymax = Sat_mean + Sat_sd), width = 0.2)+
                    theme_minimal()+
                    theme(legend.position="none",  panel.grid.major.x = element_blank())+
  #panel.grid.major.x = element_blank() removes vertical lines from the plot 
                    coord_cartesian(ylim = c(1,5))+
                    scale_fill_manual(values = c("#6baed6", "#08519c"))+
                    labs(x="Availability of technical equipment\n at home",
                         y = "Satisfaction with Home Office", 
                         caption = paste0("Point-biserial correlation was .", r_Sat_Equip,". Errorbars\n represent one SD above and below the mean."), 
                         title = "Relationship between \nequipment for and satisfaction \nwith Home Office", 
                         subtitle = "In April")+
  font_colour

HO_Sat_Equip_plot

```
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  


### Additional Information {-}  
```{r equipment 2, include=T, out.extra='style="float:left; padding:10px"', fig.height=5, fig.width=3, cache.whatever= HO_Sat_Equip_plot}

HO_Sat_Equip_plot
```

Similar to the workspace itself, having the __right equipment__ for working at home can be important for the __satisfaction__ experienced. What kind of equipment is needed can vary from job to job. For some, a simple laptop and a steady internet-connection could be enough (although granted, not always available), while others might need strong hardware, specific software, or special devices. So we just asked our participants in general __whether or not they had sufficient technical equipment__ at home, as to not assume what that should include. The barplot on the left shows the results for April.  
In general, `r HO_Equip[2]` out of `r sum(HO_Equip)` (= `r round(HO_Equip[2]*100/sum(HO_Equip), digits = 2)`%) participants indicated in April to have sufficient equipment when working from home. So, while __most people__ seemed to have the __right equipment__ at home, for the __rest__ the __insufficiency__ was associated with __lower satisfaction__. Again, statistical significance and causal analysis pending.
  
  ***
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  
&nbsp;  

# Summary and Conclusion  
As stated above, the COVID-19 Crisis brought emphasis on the topic of Home Office among other things. Coerced by the circumstances, many people started working from home. Where there were hindrances before, new possibilities arose. And while both the prevalence and permission of Home Office slowly decrease, for some the boundaries were broken for good.  
&nbsp;  
Questions arose beyond possibility and prevalence: How do people feel, when they work from home? How should the work be designed to yield best outcomes? In our short portrayal we could give first answers to these questions. In general, there is above average satisfaction with working in the Home Office. This seems to hold true regardless of childcare but is potentially influenced by the perception of self-efficacy and the presence of sufficient technical equipment. The feeling of professional isolation is relatively low, albeit a differentiation between those who work entirely from home is needed. When someone is in Home Office, having a designated spot to work from seems to be present for most, yet not given for everybody.  
&nbsp;  
We hope, that we were able to give some insights into the topic of Home Office based on our sample and to inspire future rigorous research. We believe, that with digitalization progressing relentlessly, we as researchers and practitioners of work and organizational psychology need to be ready to give well-funded advice on how to create the best circumstances for Home Office possible.  
&nbsp; 
&nbsp; 

# References {-}  
```{r clean up}
#rm(list=ls())
```

