---
title: "Personality"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 2
    include:
      after_body: footer/_footer_Richard.txt
bibliography: footer/references.bib
csl: footer/apa.csl
---
<style type="text/css">
  a {
    color: #3182bd;
    background-color: transparent;
    text-decoration: none;
  }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
library(ggplot2)
library(plyr)
library(dplyr)
library(plotly)
library(tidyr)
library(hrbrthemes)
library(gganimate)
library(inauguration)


options(scipen = 999)
data_pers = read.csv("data/data_Personality.csv")

months_PTG = c("May '20", "June '20", "July '20", "August '20", "September '20", "October '20", "November '20", "December '20",
               "January '21", "February '21", "March '21", "April '21", "May '21", "June '21")

months_lifesat = c("December '19",
  "March '20","April '20","May '20", "June '20", "July '20", "August '20", "September '20", "October '20", "November '20", "December '20",
               "January '21", "February '21", "March '21", "April '21", "May '21", "June '21")

months_Pers = c("December '19", "June '20", "March '21")
months_CSE_Proact = c("December '19", "June '20", "April '21")
months_Mind = c("December '19", "March '20", "June '20")

# Colours
Extra_col = inauguration("inauguration_2021_bernie")[1]
Agree_col = inauguration("inauguration_2021_bernie")[2]
Open_col = inauguration("inauguration_2021_bernie")[3]
Consc_col = inauguration("inauguration_2021_bernie")[4]
Emot_col = inauguration("inauguration_2021_bernie")[5]
Rest_col = "#3182bd"

font_colour = theme(text = element_text(colour = "#3e3f3a")) 
# Standard font colour of the text as indicated by the theme. Add to any gg plot to make all text in it the same colour as the "normal" body-text. MAY OVERRIDE POTENTIAL INTENDED FONTCOLOURS IN INDIVIDUAL PLOTS 

# Get the colours of the brewer-colorscale from https://colorbrewer2.org/#type=sequential&scheme=Blues&n=5

```


# Introduction  
The COVID-19 crisis can be described as a far-reaching, drastic event, that affected everybody globally in some shape or form. How people react to the crisis is affected by multiple factors, such as government restrictions and communication, social surrounding and socioeconomic status and <b>individual traits and attitudes</b>.<br>
The influence could be reciprocal, though. On the one hand, the new and unknown challenges the pandemic entailed might have been more burdensome for some people than for others, regardless of external circumstances. For example individuals with high <b>neuroticism</b>, the tendency to react emotionally to stressors and to get nervous easily, might have had less internal resources to cope with the uncertainty and additional demands that came with the pandemic. Another trait, commonly viewed as more desirable, could also be rather dysfunctional under the circumstances of the crisis: <b>Extraversion</b>. While normally the tendency to be outgoing and to connect to other people easily would be seen as helpful and attractive, in the context of contact restrictions and government mandated stay-at-home orders this personal quality could be dysfunctional and strenuous. </b><br>
On the other hand, the deep impact the crisis had on everyone's personal life might have also lead to some <b>changes</b> in personality. This could manifest in a rather negative fashion, for example through <b>higher emotional instability</b>, but also positively through a more <b>mindful</b> attitude towards oneself. This forced pause in many lives, not including those who work in essential businesses of course, might have given some people the possibility to reflect upon their daily routines and hassles. Having had to <b>take a step back</b> and sit some part of this pandemic out could have resulted in a number of people being more mindful of themselves and their needs and desires. <br>
All in all, personality certainly plays a key role in coping with the COVID-19 crisis. We were fortunate enough to have measured some aspects of personality in <b>December of 2019</b>, before the virus spread globally, and then at later points during the pandemic. This allows us to analyze the effect personality had on indicators of <b>well-being</b>, but also look at potential <b>changes of personality</b> itself. In the following sections, we present descriptive, rudimentary results from our longitudinal survey, first assessing the baseline personality of our participants, then considering possible variation over time, and finally analising the relationship of personality and life satisfaction. 

# Personality in December

## Big Five {.tabset .tabset-fade}
To assess the Big-Five personality traits we used the translated short version of the Big Five Inventory [@Rammstedt.2005]. We administered it in December '19, June '20 and March '21. <br>

### Extraversion {-}  

```{r density Extrav , include=TRUE, fig.height=4}

density_EX_T1 = ggplot(data_pers, aes(T1_extraversion))+
  theme_classic()+
  geom_histogram(binwidth=0.5,col=Extra_col, fill = Extra_col, alpha = .4)+
  geom_vline(aes(xintercept=mean(T1_extraversion, na.rm=T)), linetype="dashed", size= 0.5)+ #Line representing the mean
  labs(x="Extraversion Score", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,7,0.5), labels = seq(0,7,0.5)) +
  # Indicating the scale size and labels; seq to be read like: "Make a sequence from 0 to 100, going in steps of 10
  scale_y_continuous(breaks=seq(0, 400, 50))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour

density_EX_T1
```
<br>
Extraversion is being defined as characteristically having skills, enterprising vocational interests, participation in sports, and so on [@McCrea.1999]. All in all, it can be seen as the tendency to be outgoing and sociable. As mostly expected from personality traits, the distribution here generally follows a normal distribution, with slightly more participants indicating higher values and overall more extreme expressions. <br>  

### Agreeableness {-}
```{r density Agr , include=TRUE, fig.height=4}

density_AG_T1 = ggplot(data_pers, aes(T1_agreeableness))+
  theme_classic()+
  geom_histogram(binwidth=0.5,col=Agree_col, fill = Agree_col, alpha = .4)+
  geom_vline(aes(xintercept=mean(T1_agreeableness, na.rm=T)), linetype="dashed", size= 0.5)+ #Line representing the mean
  labs(x="Agreeableness Score", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,7,0.5), labels = seq(0,7,0.5)) +
  # Indicating the scale size and labels; seq to be read like: "Make a sequence from 0 to 100, going in steps of 10
  scale_y_continuous(breaks=seq(0, 400, 50))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour

density_AG_T1
```
<br>
Agreeableness is being defined as having forgiving attitudes, believing in cooperation and using inoffensive language [@McCrea.1999]. More generally speaking, it represents the desire or inner motive of communion and social acceptance. In our sample, it followed a normal distribution, with slightly more people indicating higher values.  

### Openness {-}  

```{r density Open , include=TRUE, fig.height=4}

density_OP_T1 = ggplot(data_pers, aes(T1_openness))+
  theme_classic()+
  geom_histogram(binwidth=0.5,col=Open_col, fill = Open_col, alpha = .4)+
  geom_vline(aes(xintercept=mean(T1_openness, na.rm=T)), linetype="dashed", size= 0.5)+ #Line representing the mean
  labs(x="Openness Score", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,7,0.5), labels = seq(0,7,0.5)) +
  # Indicating the scale size and labels; seq to be read like: "Make a sequence from 0 to 100, going in steps of 10
  scale_y_continuous(breaks=seq(0, 400, 50))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour

density_OP_T1
```
<br>
People scoring high on openness to (new) experiences tend to be interested in travel and culture, have many different hobbies and diverse vocational interests [@McCrea.1999]. It is the tendency to be curious about and having an open attitude towards culture, the arts and experiences overall. Our participants characterized themselves as being rather open. The assumption of normality might be false.  

### Conscientiousness {-}  

```{r density Consc , include=TRUE, fig.height=4}

density_CO_T1 = ggplot(data_pers, aes(T1_conscientiousness))+
  theme_classic()+
  geom_histogram(binwidth=0.5,col=Consc_col, fill =Consc_col, alpha = .4)+
  geom_vline(aes(xintercept=mean(T1_conscientiousness, na.rm=T)), linetype="dashed", size= 0.5)+ #Line representing the mean
  labs(x="Conscientiousness Score", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,7,0.5), labels = seq(0,7,0.5)) +
  # Indicating the scale size and labels; seq to be read like: "Make a sequence from 0 to 100, going in steps of 10
  scale_y_continuous(breaks=seq(0, 400, 50))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour

density_CO_T1
```
<br>
Being conscientious generally means to be organized, diligent, reliable and to make long-term plans. Scoring high on this dimension indicates a need to do everything right and on time. Our sample described itself as being rather conscientious, forming a skewed distribution favoring higher values. If that is really true or an indicator of social desirability cannot be said at this point.  

### Emotional Stability {-}  

```{r density EmStab , include=TRUE, fig.height=4}

density_ES_T1 = ggplot(data_pers, aes(T1_emostab))+
  theme_classic()+
  geom_histogram(binwidth=0.5,col=Emot_col, fill = Emot_col, alpha = .4)+
  geom_vline(aes(xintercept=mean(T1_emostab, na.rm=T)), linetype="dashed", size= 0.5)+ #Line representing the mean
  labs(x="Emotional Stability Score", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,7,0.5), labels = seq(0,7,0.5)) +
  # Indicating the scale size and labels; seq to be read like: "Make a sequence from 0 to 100, going in steps of 10
  scale_y_continuous(breaks=seq(0, 400, 50))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour

density_ES_T1
```
<br>
Emotional stability, or inversely coded as neuroticism, is regarded as having a high self esteem and optimistic attitudes [@McCrea.1999]. People with high emotional stability tend to be more resilient when facing adversity and more calm in general. As with most of the traits above, we found a rather skewed distribution, with more people indicating higher values.

## Mindfulness - Trait {.tabset .tabset-fade}

### Awareness {-}

```{r density Aware , include=TRUE, fig.height=4}

density_MAw_T1 = ggplot(data_pers, aes(T1_mindTr_aw))+
  theme_classic()+
  geom_histogram(binwidth=0.5,col="#3182bd", fill = "#6baed6", alpha = .4)+
  geom_vline(aes(xintercept=mean(T1_mindTr_aw, na.rm=T)), linetype="dashed", size= 0.5)+ #Line representing the mean
  labs(x="Mindfulness: Awareness Score", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,7,0.5), labels = seq(0,7,0.5)) +
  # Indicating the scale size and labels; seq to be read like: "Make a sequence from 0 to 100, going in steps of 10
  scale_y_continuous(breaks=seq(0, 400, 50))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour

density_MAw_T1
```

### Acceptance {-}

```{r density Accept , include=TRUE, fig.height=4}

density_MAcc_T1 = ggplot(data_pers, aes(T1_mindTr_acc))+
  theme_classic()+
  geom_histogram(binwidth=0.5,col="#3182bd", fill = "#6baed6", alpha = .4)+
  geom_vline(aes(xintercept=mean(T1_mindTr_acc, na.rm=T)), linetype="dashed", size= 0.5)+ #Line representing the mean
  labs(x="Mindfulness: Acceptance Score", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,7,0.5), labels = seq(0,7,0.5)) +
  # Indicating the scale size and labels; seq to be read like: "Make a sequence from 0 to 100, going in steps of 10
  scale_y_continuous(breaks=seq(0, 400, 50))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour

density_MAcc_T1
```

  
---  

## Proactive Personality
```{r density ProPers , include=TRUE, fig.height=4}

density_proact_T1 = ggplot(data_pers, aes(T1_proact_pers))+
  theme_classic()+
  geom_histogram(binwidth=0.5,col="#3182bd", fill = "#6baed6", alpha = .4)+
  geom_vline(aes(xintercept=mean(T1_proact_pers, na.rm=T)), linetype="dashed", size= 0.5)+ #Line representing the mean
  labs(x="Proactive Personality Score", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,7,0.5), labels = seq(0,7,0.5)) +
  # Indicating the scale size and labels; seq to be read like: "Make a sequence from 0 to 100, going in steps of 10
  scale_y_continuous(breaks=seq(0, 400, 50))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour

density_proact_T1
```

  
---  
  
## Core Self Evaluations
```{r density CSE , include=TRUE, fig.height=4}

density_CSE_T1 = ggplot(data_pers, aes(T1_CSE))+
  theme_classic()+
  geom_histogram(binwidth=0.5,col="#3182bd", fill = "#6baed6", alpha = .4)+
  geom_vline(aes(xintercept=mean(T1_CSE, na.rm=T)), linetype="dashed", size= 0.5)+ #Line representing the mean
  labs(x="Core Self Evaluations Score", y = "Amount of participants")+
  scale_x_continuous(breaks = seq(0,7,0.5), labels = seq(0,7,0.5)) +
  scale_y_continuous(breaks=seq(0, 400, 50))+
  theme(axis.text=element_text(size=12), axis.title = element_text(size = 14)) +
  font_colour

density_CSE_T1
```

  
---  
# Change over Time  

## Big Five {.tabset .tabset-fade} 

### Extraversion {-}

```{r change extr, include=TRUE}
big5_long =   reshape(
  
  select(data_pers, ID, 
         ends_with("extraversion"),
         ends_with("agreeableness"),
         ends_with("conscientiousness"),
         ends_with("openness"),
         ends_with("emostab")
         ), 
 
  varying = list(grep("extraversion", names(data_pers), value = T), 
                 grep("agreeableness", names(data_pers), value = T),
                 grep("conscientiousness", names(data_pers), value = T),
                 grep("openness", names(data_pers), value = T),
                 grep("emostab", names(data_pers), value = T)
                 ),
  
  v.names = c("Extra", "Aggree","Consc","Open","Emot"),
 
  direction = "long", 
 
  timevar = "month", 

  idvar = "ID" 
)               

big5_long$month = factor(big5_long$month, labels = months_Pers, levels = c(1,2,3))


extra_change = ggplot(big5_long, aes(x=month, y = Extra)) +
  geom_violin(trim = T,col= Extra_col ) +
  geom_jitter(width = 0.1, size = 0.05,col= Extra_col, alpha = 0.3) +
  
  geom_line(aes(group=1, color = Extra_col), col= Extra_col, size = 1, stat = "summary", fun = mean)+
  geom_point(col= Extra_col, size = 3, stat = "summary", fun = mean)+
  geom_errorbar(width=.1,position=position_dodge(0.05), col =Extra_col, stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1)) +
  
  coord_cartesian(ylim = c(1,7))+
  theme_minimal()+
  scale_x_discrete(limits = months_Pers, name ="" )+
  scale_y_continuous(breaks = seq(1,7,1), name = "Extraversion")+
  font_colour

extra_change

```

### Agreeableness {-}

```{r change agree, include=TRUE, fig.show='hold'}
agree_change = ggplot(big5_long, aes(x=month, y = Aggree)) +
  geom_violin(trim = T,col= Agree_col ) +
  geom_jitter(width = 0.1, size = 0.05,col= Agree_col, alpha = 0.3) +
  
  geom_line(aes(group=1, color = Agree_col), col= Agree_col, size = 1, stat = "summary", fun = mean)+
  geom_point(col= Agree_col, size = 3, stat = "summary", fun = mean)+
  geom_errorbar(width=.1,position=position_dodge(0.05), col = Agree_col, stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1)) +
  
  coord_cartesian(ylim = c(1,7))+
  theme_minimal()+
  scale_x_discrete(limits = months_Pers, name ="" )+
  scale_y_continuous(breaks = seq(1,7,1), name = "Agreableness")+
  font_colour

agree_change
```

### Openness {-}

```{r change open, include=TRUE, fig.show='hold'}
open_change = ggplot(big5_long, aes(x=month, y = Open)) +
  geom_violin(trim = T,col= Open_col ) +
  geom_jitter(width = 0.1, size = 0.05,col= Open_col, alpha = 0.3) +
  
  geom_line(aes(group=1, color = Open_col), col= Open_col, size = 1, stat = "summary", fun = mean)+
  geom_point(col= Open_col, size = 3, stat = "summary", fun = mean)+
  geom_errorbar(width=.1,position=position_dodge(0.05), col = Open_col, stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1)) +
  
  coord_cartesian(ylim = c(1,7))+
  theme_minimal()+
  scale_x_discrete(limits = months_Pers, name ="" )+
  scale_y_continuous(breaks = seq(1,7,1), name = "Openness")+
  font_colour

open_change
```


### Conscientiousness {-}

```{r change consc, include=TRUE, fig.show='hold'}
consc_change = ggplot(big5_long, aes(x=month, y = Consc)) +
  geom_violin(trim = T,col= Consc_col ) +
  geom_jitter(width = 0.1, size = 0.05,col= Consc_col, alpha = 0.3) +
  
  geom_line(aes(group=1, color = Consc_col), col= Consc_col, size = 1, stat = "summary", fun = mean)+
  geom_point(col= Consc_col, size = 3, stat = "summary", fun = mean)+
  geom_errorbar(width=.1,position=position_dodge(0.05), col = Consc_col, stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1)) +
  
  coord_cartesian(ylim = c(1,7))+
  theme_minimal()+
  scale_x_discrete(limits = months_Pers, name ="" )+
  scale_y_continuous(breaks = seq(1,7,1), name = "Conscientiousness")+
  font_colour

consc_change
```


### Emotional Stability {-}

```{r change emot, include=TRUE, fig.show='hold'}
emot_change = ggplot(big5_long, aes(x=month, y = Emot)) +
  geom_violin(trim = T,col= Emot_col ) +
  geom_jitter(width = 0.1, size = 0.05,col= Emot_col, alpha = 0.3) +
  
  geom_line(aes(group=1, color = Emot_col), col= Emot_col, size = 1, stat = "summary", fun = mean)+
  geom_point(col= Emot_col, size = 3, stat = "summary", fun = mean)+
  geom_errorbar(width=.1,position=position_dodge(0.05), col = Emot_col, stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1)) +
  
  coord_cartesian(ylim = c(1,7))+
  theme_minimal()+
  scale_x_discrete(limits = months_Pers, name ="" )+
  scale_y_continuous(breaks = seq(1,7,1), name = "Emotional Stability")+
  font_colour

emot_change
```

## Mindfulness - Trait {.tabset .tabset-fade}

### Awareness {-}
```{r change aware, include=TRUE}
Mind_long =   reshape(

  select(data_pers, ID,
         ends_with("_mind_aware"),
         ends_with("_mind_accept")
         ),

  varying = list(c("T1_mind_aware","T2_mind_aware","T5_mind_aware"),
                 c("T1_mind_accept","T2_mind_accept","T5_mind_accept")
                 ),

  v.names = c("Mind_Aw","Mind_Ac"),

  direction = "long",

  timevar = "month",

  idvar = "ID"
)

Mind_long$month = factor(Mind_long$month, labels = months_Mind)

aware_change = ggplot(Mind_long, aes(x=month, y = Mind_Aw)) +
  geom_violin(trim = T,col= Rest_col ) +
  geom_jitter(width = 0.1, size = 0.05,col= Rest_col, alpha = 0.3) +
  
  geom_line(aes(group=1, color = Rest_col), col= Rest_col, size = 1, stat = "summary", fun = mean)+
  geom_point(col= Rest_col, size = 3, stat = "summary", fun = mean)+
  geom_errorbar(width=.1,position=position_dodge(0.05), col =Rest_col, stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1)) +
  
  coord_cartesian(ylim = c(1,7))+
  theme_minimal()+
  scale_x_discrete(limits = months_Mind, name ="" )+
  scale_y_continuous(breaks = seq(1,7,1), name = "Mindfulness: Awareness")+
  font_colour

aware_change
```

### Acceptance {-}
```{r change acc, include=TRUE}

accept_change = ggplot(Mind_long, aes(x=month, y = Mind_Ac)) +
  geom_violin(trim = T,col= Rest_col ) +
  geom_jitter(width = 0.1, size = 0.05,col= Rest_col, alpha = 0.3) +
  
  geom_line(aes(group=1, color = Rest_col), col= Rest_col, size = 1, stat = "summary", fun = mean)+
  geom_point(col= Rest_col, size = 3, stat = "summary", fun = mean)+
  geom_errorbar(width=.1,position=position_dodge(0.05), col =Rest_col, stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1)) +
  
  coord_cartesian(ylim = c(1,7))+
  theme_minimal()+
  scale_x_discrete(limits = months_Mind, name ="" )+
  scale_y_continuous(breaks = seq(1,7,1), name = "Mindfulness: Acceptance")+
  font_colour

accept_change
```

## Proactive Personality
```{r change proact, include=TRUE}
CES_Proact_long =   reshape(

  select(data_pers, ID,
         ends_with("proact_pers"),
         ends_with("CSE")
         ),

  varying =  list(grep("CSE", names(data_pers), value = T),
                 grep("proact", names(data_pers), value = T)
                 ),

  v.names = c("CSE","Proact"),

  direction = "long",

  timevar = "month",

  idvar = "ID"
)

CES_Proact_long$month = factor(CES_Proact_long$month, labels = months_CSE_Proact)

proact_change = ggplot(CES_Proact_long, aes(x=month, y = Proact)) +
  geom_violin(trim = T,col= Rest_col ) +
  geom_jitter(width = 0.1, size = 0.05,col= Rest_col, alpha = 0.3) +
  
  geom_line(aes(group=1, color = Rest_col), col= Rest_col, size = 1, stat = "summary", fun = mean)+
  geom_point(col= Rest_col, size = 3, stat = "summary", fun = mean)+
  geom_errorbar(width=.1,position=position_dodge(0.05), col =Rest_col, stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1)) +
  
  coord_cartesian(ylim = c(1,7))+
  theme_minimal()+
  scale_x_discrete(limits = months_CSE_Proact, name ="" )+
  scale_y_continuous(breaks = seq(1,7,1), name = "Proactive Personality")+
  font_colour

proact_change
```

## Core Self Evaluations
```{r change CSE, include=TRUE}

CSE_change = ggplot(CES_Proact_long, aes(x=month, y = CSE)) +
  geom_violin(trim = T,col= Rest_col ) +
  geom_jitter(width = 0.1, size = 0.05,col= Rest_col, alpha = 0.3) +
  
  geom_line(aes(group=1, color = Rest_col), col= Rest_col, size = 1, stat = "summary", fun = mean)+
  geom_point(col= Rest_col, size = 3, stat = "summary", fun = mean)+
  geom_errorbar(width=.1,position=position_dodge(0.05), col =Rest_col, stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1)) +
  
  coord_cartesian(ylim = c(1,7))+
  theme_minimal()+
  scale_x_discrete(limits = months_CSE_Proact, name ="" )+
  scale_y_continuous(breaks = seq(1,7,1), name = "Core Self Evaluations")+
  font_colour

CSE_change
```

Further Ideas: 

PTG over Time


# Life Satisfaction depending on Traits 

```{r sat, include = TRUE, cache.whatever = months_lifesat}
lifesat_long = reshape(
  select(data_pers, 
         ID, 
         T1_extraversion,
         T1_agreeableness,
         T1_conscientiousness,
         T1_openness,
         T1_emostab,
         T1_CSE,
         T1_proact_pers,
         T1_mind_aware,
         T1_mind_accept,
         ends_with("life_sat")
         ),

  varying =  grep("life", names(data_pers), value = T),

  v.names = "Life_Sat",

  direction = "long",

  timevar = "month",

  idvar = "ID"
  
)

lifesat_long$month = factor(lifesat_long$month, labels = months_lifesat)

pers_higlow = data_pers %>% dplyr::summarise_at(
  vars(
    T1_extraversion,
    T1_agreeableness,
    T1_conscientiousness,
    T1_openness,
    T1_emostab,
    T1_CSE,
    T1_proact_pers,
    T1_mind_aware,
    T1_mind_accept
    ), 
  list(high =~ mean(.x, na.rm = T) + sd(.x, na.rm = T), 
       low =~ mean(.x, na.rm = T) - sd(.x, na.rm = T)))

## Making new grouping Variables
lifesat_long =lifesat_long %>% mutate(
    Extraversion = case_when(
      T1_extraversion >= pers_higlow$T1_extraversion_high & !is.na(T1_extraversion) ~ "high",
      T1_extraversion <= pers_higlow$T1_extraversion_low & !is.na(T1_extraversion) ~ "low",
      T1_extraversion < pers_higlow$T1_extraversion_high & T1_extraversion > pers_higlow$T1_extraversion_low & !is.na(T1_extraversion) ~ "average"
    ),
    
    Agreeableness = case_when(
      T1_agreeableness >= pers_higlow$T1_agreeableness_high ~ "high",
      T1_agreeableness <= pers_higlow$T1_agreeableness_low  ~ "low",
      T1_agreeableness < pers_higlow$T1_agreeableness_high & T1_agreeableness > pers_higlow$T1_agreeableness_low ~ "average"
    ),
    
    Openness = case_when(
      T1_openness >= pers_higlow$T1_openness_high ~ "high",
      T1_openness <= pers_higlow$T1_openness_low ~ "low",
      T1_openness < pers_higlow$T1_openness_high & T1_openness > pers_higlow$T1_openness_low ~ "average"
    ),
    
    Conscientiousness = case_when(
      T1_conscientiousness >= pers_higlow$T1_conscientiousness_high ~ "high",
      T1_conscientiousness <= pers_higlow$T1_conscientiousness_low ~ "low",
      T1_conscientiousness < pers_higlow$T1_conscientiousness_high & T1_conscientiousness > pers_higlow$T1_conscientiousness_low ~ "average"
    ),
    
    Stability = case_when(
      T1_emostab >= pers_higlow$T1_emostab_high ~ "high",
      T1_emostab <= pers_higlow$T1_emostab_low ~ "low",
      T1_emostab < pers_higlow$T1_emostab_high & T1_emostab > pers_higlow$T1_emostab_low ~ "average"
    ),
    
    Mind_Aware = case_when(
      T1_mind_aware >= pers_higlow$T1_mind_aware_high ~ "high",
      T1_mind_aware <= pers_higlow$T1_mind_aware_low ~ "low",
      T1_mind_aware < pers_higlow$T1_mind_aware_high & T1_mind_aware > pers_higlow$T1_mind_aware_low ~ "average"
    ),
    
    Mind_Accept = case_when(
      T1_mind_accept >= pers_higlow$T1_mind_accept_high ~ "high",
      T1_mind_accept <= pers_higlow$T1_mind_accept_low ~ "low",
      T1_mind_accept < pers_higlow$T1_mind_accept_high & T1_mind_accept > pers_higlow$T1_mind_accept_low ~ "average"
    ),
    
    CSE = case_when(
      T1_CSE >= pers_higlow$T1_CSE_high ~ "high",
      T1_CSE <= pers_higlow$T1_CSE_low ~ "low",
      T1_CSE < pers_higlow$T1_CSE_high & T1_CSE > pers_higlow$T1_CSE_low ~ "average"
    ),
    
    Proact_Pers = case_when(
      T1_proact_pers >= pers_higlow$T1_proact_pers_high ~ "high",
      T1_proact_pers <= pers_higlow$T1_proact_pers_low ~ "low",
      T1_proact_pers < pers_higlow$T1_proact_pers_high & T1_proact_pers > pers_higlow$T1_proact_pers_low ~ "average"
    ),
    
    
)

lifesat_long[13:21] =  lapply(select(lifesat_long, Extraversion:Proact_Pers),factor, levels =c("low", "average", "high") , labels =c("Low", "Average", "High"))

lifesat_long = lifesat_long[lifesat_long$Life_Sat > 0,]

lifesat = ggplot(lifesat_long, aes(x=month, y = Life_Sat)) +
  geom_line(aes(group = 1),col= "#74c476", size = 1.5, stat = "summary", fun = mean)+
  geom_point(size = 3,col="#74c476", stat = "summary", fun = mean)+
  geom_ribbon(aes(group = 1),fill="#74c476", alpha=0.4, stat = "summary", fun.data = "mean_sdl", fun.args = list(mult = 1) ) +
  
  scale_color_manual(values = "#74c476")+
  
  coord_cartesian(ylim = c(3,7))+
  theme_minimal()+
  scale_x_discrete(limits = months_lifesat, name ="" )+
  scale_y_continuous(breaks = seq(3,7,1), name = "Life Satisfaction")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(caption = "Note: Ribbon represents one SD above and below the mean.")+
  font_colour

lifesat
```


## Big Five {.tabset .tabset-fade} 

### Extraversion {-}

```{r sat extr, include=TRUE, cache.whatever = lifesat}
Extra_col_3 = c("#8478ca","#5445b1","#3a307a")

lifesat_extra = ggplot(lifesat_long[is.na(lifesat_long$Extraversion)==F,], aes(x=month, y = Life_Sat)) +
  geom_line(aes(group = Extraversion, color = Extraversion), size = 1, stat = "summary", fun = mean)+
  geom_point(aes(color = Extraversion), size = 3, stat = "summary", fun = mean)+
  scale_color_manual(values = Extra_col_3)+
  
  coord_cartesian(ylim = c(4,6))+
  theme_minimal()+
  scale_x_discrete(limits = months_lifesat, name ="" )+
  scale_y_continuous(breaks = seq(4,6,0.5), name = "Life Satisfaction")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position = "top")+
  labs(caption = "Note: Borders for average were defined as one SD above and below the mean.")+
  font_colour

lifesat_extra

```

### Agreeableness {-}

```{r sat agree, include=TRUE, cache.whatever = lifesat}
Agree_col_3 = c("#ac937e","#876d57","#584739")

lifesat_agree = ggplot(lifesat_long[is.na(lifesat_long$Agreeableness)==F,], aes(x=month, y = Life_Sat)) +
  geom_line(aes(group = Agreeableness, color = Agreeableness), size = 1, stat = "summary", fun = mean)+
  geom_point(aes(color = Agreeableness), size = 3, stat = "summary", fun = mean)+
  scale_color_manual(values = Agree_col_3)+
  
  coord_cartesian(ylim = c(4,6))+
  theme_minimal()+
  scale_x_discrete(limits = months_lifesat, name ="" )+
  scale_y_continuous(breaks = seq(4,6,0.5), name = "Life Satisfaction")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position = "top")+
  labs(caption = "Note: Borders for average were defined as one SD above and below the mean.")+
  font_colour

lifesat_agree
```

### Openness {-}

```{r sat open, include=TRUE, cache.whatever = lifesat}
Open_col_3 = c("#a4bfca","#749dae","#4f7687")

lifesat_open = ggplot(lifesat_long[is.na(lifesat_long$Openness)==F,], aes(x=month, y = Life_Sat)) +
  geom_line(aes(group = Openness, color = Openness), size = 1, stat = "summary", fun = mean)+
  geom_point(aes(color = Openness), size = 3, stat = "summary", fun = mean)+
  scale_color_manual(values = Open_col_3)+
  
  coord_cartesian(ylim = c(4,6))+
  theme_minimal()+
  scale_x_discrete(limits = months_lifesat, name ="" )+
  scale_y_continuous(breaks = seq(4,6,0.5), name = "Life Satisfaction")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position = "top")+
  labs(caption = "Note: Borders for average were defined as one SD above and below the mean.")+
  font_colour

lifesat_open
```


### Conscientiousness {-}

```{r sat consc, include=TRUE, cache.whatever = lifesat}
Consc_col_3 = c("#fae5c9","#f3c483","#eca33d")

lifesat_consc = ggplot(lifesat_long[is.na(lifesat_long$Conscientiousness)==F,], aes(x=month, y = Life_Sat)) +
  geom_line(aes(group = Conscientiousness, color = Conscientiousness), size = 1, stat = "summary", fun = mean)+
  geom_point(aes(color = Conscientiousness), size = 3, stat = "summary", fun = mean)+
  scale_color_manual(values = Consc_col_3)+
  
  coord_cartesian(ylim = c(4,6))+
  theme_minimal()+
  scale_x_discrete(limits = months_lifesat, name ="" )+
  scale_y_continuous(breaks = seq(4,6,0.5), name = "Life Satisfaction")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position = "top")+
  labs(caption = "Note: Borders for average were defined as one SD above and below the mean.")+
  font_colour

lifesat_consc
```


### Emotional Stability {-}

```{r sat emot, include=TRUE, cache.whatever = lifesat}
Emot_col_3 = c("#982b54","#5c1a33","#200912")

lifesat_emot = ggplot(lifesat_long[is.na(lifesat_long$Stability)==F,], aes(x=month, y = Life_Sat)) +
  geom_line(aes(group = Stability, color = Stability), size = 1, stat = "summary", fun = mean)+
  geom_point(aes(color = Stability), size = 3, stat = "summary", fun = mean)+
  scale_color_manual(values = Emot_col_3)+
  
  coord_cartesian(ylim = c(4,6))+
  theme_minimal()+
  scale_x_discrete(limits = months_lifesat, name ="" )+
  scale_y_continuous(breaks = seq(4,6,0.5), name = "Life Satisfaction")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position = "top")+
  labs(caption = "Note: Borders for average were defined as one SD above and below the mean.", color = "Emotional Stability")+
  font_colour

lifesat_emot
```

## Mindfulness - Trait {.tabset .tabset-fade}

### Awareness {-}
```{r sat aware, include=TRUE, cache.whatever = lifesat}
Rest_col_3 = c("#64a6d7","#3182bd","#215880")

lifesat_aware = ggplot(lifesat_long[is.na(lifesat_long$Mind_Aware)==F,], aes(x=month, y = Life_Sat)) +
  geom_line(aes(group = Mind_Aware, color = Mind_Aware), size = 1, stat = "summary", fun = mean)+
  geom_point(aes(color = Mind_Aware), size = 3, stat = "summary", fun = mean)+
  scale_color_manual(values = Rest_col_3)+
  
  coord_cartesian(ylim = c(4,6))+
  theme_minimal()+
  scale_x_discrete(limits = months_lifesat, name ="" )+
  scale_y_continuous(breaks = seq(4,6,0.5), name = "Life Satisfaction")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position = "top")+
  labs(caption = "Note: Borders for average were defined as one SD above and below the mean.", color = "Mindfulness - Awareness")+
  font_colour

lifesat_aware
```

### Acceptance {-}
```{r sat acc, include=TRUE, cache.whatever = lifesat}
lifesat_acc = ggplot(lifesat_long[is.na(lifesat_long$Mind_Accept)==F,], aes(x=month, y = Life_Sat)) +
  geom_line(aes(group = Mind_Accept, color = Mind_Accept), size = 1, stat = "summary", fun = mean)+
  geom_point(aes(color = Mind_Accept), size = 3, stat = "summary", fun = mean)+
  scale_color_manual(values = Rest_col_3)+
  
  coord_cartesian(ylim = c(4,6))+
  theme_minimal()+
  scale_x_discrete(limits = months_lifesat, name ="" )+
  scale_y_continuous(breaks = seq(4,6,0.5), name = "Life Satisfaction")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position = "top")+
  labs(caption = "Note: Borders for average were defined as one SD above and below the mean.", color = "Mindfulness - Acceptance")+
  font_colour

lifesat_acc

```

## Proactive Personality
```{r sat proact, include=TRUE, cache.whatever = lifesat}
lifesat_proact = ggplot(lifesat_long[is.na(lifesat_long$Proact_Pers)==F,], aes(x=month, y = Life_Sat)) +
  geom_line(aes(group = Proact_Pers, color = Proact_Pers), size = 1, stat = "summary", fun = mean)+
  geom_point(aes(color = Proact_Pers), size = 3, stat = "summary", fun = mean)+
  scale_color_manual(values = Rest_col_3)+
  
  coord_cartesian(ylim = c(4,6))+
  theme_minimal()+
  scale_x_discrete(limits = months_lifesat, name ="" )+
  scale_y_continuous(breaks = seq(4,6,0.5), name = "Life Satisfaction")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position = "top")+
  labs(caption = "Note: Borders for average were defined as one SD above and below the mean.", color = "Proactive Personality")+
  font_colour

lifesat_proact
```

## Core Self Evaluations
```{r sat CSE, include=TRUE, cache.whatever = lifesat}
lifesat_CSE = ggplot(lifesat_long[is.na(lifesat_long$CSE)==F,], aes(x=month, y = Life_Sat)) +
  geom_line(aes(group = CSE, color = CSE), size = 1, stat = "summary", fun = mean)+
  geom_point(aes(color = CSE), size = 3, stat = "summary", fun = mean)+
  scale_color_manual(values = Rest_col_3)+
  
  coord_cartesian(ylim = c(3.5,6.5))+
  theme_minimal()+
  scale_x_discrete(limits = months_lifesat, name ="" )+
  scale_y_continuous(breaks = seq(3.5,6.5,0.5), name = "Life Satisfaction")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position = "top")+
  labs(caption = "Note: Borders for average were defined as one SD above and below the mean.", color = "Core Self Evaluations")+
  font_colour

lifesat_CSE

```



